
# Simulation Study: Bayesian Dynamic Network for Traffic Data

This vignette demonstrates a complete simulation study using `bdynets` on synthetic traffic data from a grid road network.

```{r setup, include = FALSE}
library(bdynets)
library(ggplot2)
library(dplyr)
library(tidyr)
library(patchwork)
library(RColorBrewer)

set.seed(20260509)
```

---

## 1. Synthetic Data Generation

### 1.1 Create 5×5 Grid Road Network

```{r generate-network}
generate_grid_network <- function(rows = 5, cols = 5) {
  n_nodes <- rows * cols
  
  ## Create node coordinates
  nodes <- expand.grid(row = 1:rows, col = 1:cols)
  nodes$node_id <- 1:n_nodes
  
  ## Create directed edges (each node connects to adjacent nodes)
  edges <- data.frame(
    from = integer(),
    to = integer(),
    direction = character()
  )
  
  for (i in 1:rows) {
    for (j in 1:cols) {
      node_id <- (i - 1) * cols + j
      
      ## Right neighbor
      if (j < cols) {
        edges <- rbind(edges, data.frame(
          from = node_id,
          to = node_id + 1,
          direction = "horizontal"
        ))
        edges <- rbind(edges, data.frame(
          from = node_id + 1,
          to = node_id,
          direction = "horizontal"
        ))
      }
      
      ## Down neighbor
      if (i < rows) {
        edges <- rbind(edges, data.frame(
          from = node_id,
          to = node_id + cols,
          direction = "vertical"
        ))
        edges <- rbind(edges, data.frame(
          from = node_id + cols,
          to = node_id,
          direction = "vertical"
        ))
      }
    }
  }
  
  list(
    nodes = nodes,
    edges = edges,
    n_nodes = n_nodes,
    n_edges = nrow(edges)
  )
}

network <- generate_grid_network(5, 5)
cat("Network:", network$n_nodes, "nodes,", network$n_edges, "edges\n")
```

### 1.2 Create Time Structure (4 weeks, 48 intervals/day)

```{r time-structure}
## Time parameters
intervals_per_day <- 48  # 30-minute intervals
n_days <- 28             # 4 weeks
TT <- intervals_per_day * n_days  # Total time steps

## Create time index
time_index <- data.frame(
  t = 1:TT,
  day = rep(1:n_days, each = intervals_per_day),
  interval = rep(1:intervals_per_day, n_days),
  hour = rep(0:23, each = 2, times = n_days),
  day_of_week = rep(1:7, each = intervals_per_day, times = 4)
)

## Add peak hour indicators
time_index$is_morning_peak <- time_index$hour %in% c(7, 8, 9)
time_index$is_evening_peak <- time_index$hour %in% c(17, 18, 19)
time_index$is_weekend <- time_index$day_of_week %in% c(6, 7)
```

### 1.3 Generate True Cluster Structure

```{r true-clusters}
## True number of clusters
K_true <- 3

## Define cluster characteristics (traffic patterns)
## Cluster 1: Low traffic (residential areas)
## Cluster 2: Medium traffic (suburban connectors)
## Cluster 3: High traffic (major arteries/downtown)

cluster_profiles <- list(
  ## Cluster 1: Low, flat pattern
  list(
    base = 2,
    morning_peak = 1.5,
    evening_peak = 1.3,
    weekend_effect = 0.7
  ),
  ## Cluster 2: Medium, bimodal pattern
  list(
    base = 5,
    morning_peak = 2.5,
    evening_peak = 2.0,
    weekend_effect = 0.6
  ),
  ## Cluster 3: High, strong peaks
  list(
    base = 10,
    morning_peak = 3.5,
    evening_peak = 3.0,
    weekend_effect = 0.5
  )
)

## Assign edges to clusters (with some spatial structure)
set.seed(20260509)
edge_cluster <- rep(1:K_true, length.out = network$n_edges)
## Add some spatial correlation
edge_cluster <- sample(edge_cluster, replace = FALSE)

## Create design matrix Fmat (TT x p)
p <- 4  # Intercept, morning peak, evening peak, weekend
Fmat <- model.matrix(
  ~ is_morning_peak + is_evening_peak + is_weekend,
  data = time_index
)
colnames(Fmat) <- c("intercept", "morning_peak", "evening_peak", "weekend")
```

### 1.4 Generate True Parameters

```{r true-parameters}
## True theta parameters (K x TT x p)
theta_true <- array(0, dim = c(K_true, TT, p))

for (k in 1:K_true) {
  profile <- cluster_profiles[[k]]
  
  ## Base intercept
  theta_true[k, , 1] <- log(profile$base)
  
  ## Peak effects
  theta_true[k, , 2] <- log(profile$morning_peak)
  theta_true[k, , 3] <- log(profile$evening_peak)
  theta_true[k, , 4] <- log(profile$weekend_effect)
}

## Add small time-varying component (smooth variation)
for (k in 1:K_true) {
  time_trend <- 0.1 * sin(2 * pi * (1:TT) / intervals_per_day)
  theta_true[k, , 1] <- theta_true[k, , 1] + time_trend
}

## True cluster probabilities
pi_true <- c(0.4, 0.35, 0.25)

## Assign edges to clusters
Z_true <- edge_cluster
```

### 1.5 Simulate Count Data

```{r simulate-data}
## Compute intensity for each edge at each time point
lambda_matrix <- matrix(0, nrow = network$n_edges, ncol = TT)
for (e in 1:network$n_edges) {
  k <- Z_true[e]
  eta_e <- rowSums(Fmat * theta_true[k, , ])
  lambda_matrix[e, ] <- exp(eta_e)
}

## Simulate Poisson counts
Y <- matrix(0, nrow = network$n_edges, ncol = TT)
for (e in 1:network$n_edges) {
  Y[e, ] <- rpois(TT, lambda_matrix[e, ])
}

cat("Data dimensions:", nrow(Y), "edges ×", ncol(Y), "time points\n")
cat("Total observations:", length(Y), "\n")
cat("Mean count:", round(mean(Y), 2), "\n")
cat("Max count:", max(Y), "\n")
```

---

## 2. Data Visualization

### 2.1 Network Structure

```{r plot-network}
plot_network_structure <- function(network, Z_true) {
  nodes <- network$nodes
  edges <- network$edges
  edges$cluster <- Z_true
  
  ## Node positions
  node_positions <- nodes %>%
    mutate(
      x = col,
      y = -row  ## Flip y for plotting
    )
  
  ## Edge data with cluster colors
  edge_data <- edges %>%
    left_join(node_positions, by = c("from" = "node_id")) %>%
    rename(x1 = x, y1 = y) %>%
    left_join(node_positions, by = c("to" = "node_id")) %>%
    rename(x2 = x, y2 = y)
  
  cluster_colors <- brewer.pal(max(Z_true), "Set2")
  
  ggplot() +
    geom_segment(
      data = edge_data,
      aes(x = x1, y = y1, xend = x2, yend = y2, color = factor(cluster)),
      linewidth = 1.2,
      arrow = arrow(length = unit(0.15, "cm"), type = "closed")
    ) +
    geom_point(
      data = node_positions,
      aes(x = x, y = y),
      size = 4,
      color = "darkgray",
      shape = 21,
      fill = "white"
    ) +
    geom_text(
      data = node_positions,
      aes(x = x, y = y, label = node_id),
      size = 3,
      color = "black"
    ) +
    scale_color_manual(
      name = "Cluster",
      values = cluster_colors,
      labels = paste("Cluster", 1:max(Z_true))
    ) +
    coord_fixed() +
    theme_minimal() +
    theme(
      axis.title = element_blank(),
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      panel.grid = element_blank(),
      legend.position = "bottom"
    ) +
    labs(title = "5×5 Grid Road Network with True Cluster Assignments")
}

p_network <- plot_network_structure(network, Z_true)
p_network
```

### 2.2 Time Series of Traffic Counts

```{r plot-timeseries}
plot_traffic_timeseries <- function(Y, time_index, Z_true, K) {
  ## Convert to long format
  Y_long <- as.data.frame(Y) %>%
    mutate(edge = 1:nrow(Y)) %>%
    pivot_longer(
      cols = -edge,
      names_to = "time",
      values_to = "count"
    ) %>%
    mutate(
      time = as.numeric(gsub("V", "", time)),
      cluster = Z_true[edge]
    ) %>%
    left_join(time_index, by = c("time" = "t"))
  
  ## Aggregate by cluster and time
  cluster_summary <- Y_long %>%
    group_by(cluster, time) %>%
    summarize(
      mean_count = mean(count),
      sd_count = sd(count),
      .groups = "drop"
    )
  
  cluster_colors <- brewer.pal(K, "Set2")
  
  ggplot(cluster_summary, aes(x = time, y = mean_count, color = factor(cluster))) +
    geom_line(linewidth = 1) +
    geom_ribbon(
      aes(ymin = mean_count - sd_count, ymax = mean_count + sd_count, fill = factor(cluster)),
      alpha = 0.2,
      color = NA
    ) +
    scale_color_manual(
      name = "Cluster",
      values = cluster_colors,
      labels = paste("Cluster", 1:K)
    ) +
    scale_fill_manual(
      name = "Cluster",
      values = cluster_colors,
      labels = paste("Cluster", 1:K),
      guide = "none"
    ) +
    geom_vline(
      xintercept = seq(1, TT, by = intervals_per_day),
      linetype = "dashed",
      alpha = 0.3
    ) +
    labs(
      title = "Traffic Count Time Series by Cluster",
      subtitle = "Mean ± SD across edges in each cluster",
      x = "Time Step (30-min intervals)",
      y = "Mean Count"
    ) +
    theme_minimal() +
    theme(
      legend.position = "bottom",
      panel.grid.minor = element_blank()
    )
}

p_timeseries <- plot_traffic_timeseries(Y, time_index, Z_true, K_true)
p_timeseries
```

### 2.3 Daily Pattern Heatmap

```{r plot-heatmap}
plot_daily_pattern <- function(Y, time_index, Z_true, K) {
  Y_long <- as.data.frame(Y) %>%
    mutate(edge = 1:nrow(Y)) %>%
    pivot_longer(
      cols = -edge,
      names_to = "time",
      values_to = "count"
    ) %>%
    mutate(
      time = as.numeric(gsub("V", "", time)),
      cluster = Z_true[edge]
    ) %>%
    left_join(time_index, by = c("time" = "t"))
  
  ## Aggregate by cluster, hour, and day type
  pattern_summary <- Y_long %>%
    group_by(cluster, hour, is_weekend) %>%
    summarize(
      mean_count = mean(count),
      .groups = "drop"
    ) %>%
    mutate(
      day_type = ifelse(is_weekend, "Weekend", "Weekday")
    )
  
  ggplot(pattern_summary, aes(x = hour, y = factor(cluster), fill = mean_count)) +
    geom_tile(color = "white", linewidth = 0.5) +
    geom_text(
      aes(label = round(mean_count, 1)),
      size = 3,
      color = "black"
    ) +
    facet_wrap(~ day_type, ncol = 2) +
    scale_fill_gradientn(
      name = "Mean Count",
      colors = brewer.pal(9, "YlOrRd"),
      na.value = "white"
    ) +
    scale_y_discrete(labels = function(x) paste("Cluster", x)) +
    labs(
      title = "Daily Traffic Patterns by Cluster",
      subtitle = "Average count by hour and day type",
      x = "Hour of Day",
      y = "Cluster"
    ) +
    theme_minimal() +
    theme(
      legend.position = "right",
      panel.grid = element_blank(),
      axis.text.y = element_text(size = 10)
    )
}

p_heatmap <- plot_daily_pattern(Y, time_index, Z_true, K_true)
p_heatmap
```

---

## 3. Run MCMC

```{r run-mcmc, eval=FALSE}
## MCMC settings
n_iter <- 800
burn <- 400
K_fit <- K_true

## Prior settings
alpha_pi <- rep(1, K_fit)
m0_fit <- c(log(mean(Y) + 0.1), 0, 0, 0)
C0_fit <- diag(4) * 5
G_fit <- diag(4)
W_fit <- diag(4) * 0.01
r_tune <- (max(Y) + sqrt(max(Y)) * 3) * 50

cat("Running MCMC with", n_iter, "iterations...\n")

## Run Gibbs sampler
mcmc_result <- bdynets::gibbs_sampler(
  Y = Y,
  Fmat = Fmat,
  K = K_fit,
  n_iter = n_iter,
  burn = burn,
  alpha_pi = alpha_pi,
  m0 = m0_fit,
  C0 = C0_fit,
  G = G_fit,
  W = W_fit,
  r_tune = r_tune,
  Z_true = Z_true,
  relabel_freq = 1,
  print_freq = 100,
  store_theta = TRUE,
  seed = 20260509
)

cat("MCMC completed in", round(mcmc_result$settings$total_time, 2), "seconds\n")
```

---

## 4. MCMC Diagnostics

### 4.1 Trace Plots

```{r plot-trace, eval=FALSE}
plot_trace_diagnostics <- function(mcmc_result) {
  burn <- mcmc_result$settings$burn
  keep_idx <- seq(burn + 1, mcmc_result$settings$n_iter)
  K <- mcmc_result$settings$K
  
  ## Cluster probabilities
  pi_long <- as.data.frame(mcmc_result$pi[keep_idx, ]) %>%
    mutate(iteration = keep_idx) %>%
    pivot_longer(
      cols = -iteration,
      names_to = "cluster",
      values_to = "value"
    ) %>%
    mutate(cluster = gsub("V", "", cluster))
  
  cluster_colors <- brewer.pal(K, "Set2")
  
  p_pi <- ggplot(pi_long, aes(x = iteration, y = value, color = cluster)) +
    geom_line(alpha = 0.7, linewidth = 0.8) +
    scale_color_manual(
      name = "Cluster",
      values = cluster_colors,
      labels = paste("Cluster", 1:K)
    ) +
    labs(
      title = "Trace Plot: Cluster Probabilities (π)",
      x = "Iteration",
      y = "Probability"
    ) +
    theme_minimal() +
    theme(
      legend.position = "bottom",
      panel.grid.minor = element_blank()
    )
  
  ## Cluster sizes
  size_long <- as.data.frame(mcmc_result$size[keep_idx, ]) %>%
    mutate(iteration = keep_idx) %>%
    pivot_longer(
      cols = -iteration,
      names_to = "cluster",
      values_to = "value"
    ) %>%
    mutate(cluster = gsub("V", "", cluster))
  
  p_size <- ggplot(size_long, aes(x = iteration, y = value, color = cluster)) +
    geom_line(alpha = 0.7, linewidth = 0.8) +
    scale_color_manual(
      name = "Cluster",
      values = cluster_colors,
      labels = paste("Cluster", 1:K),
      guide = "none"
    ) +
    labs(
      title = "Trace Plot: Cluster Sizes",
      x = "Iteration",
      y = "Number of Edges"
    ) +
    theme_minimal() +
    theme(
      legend.position = "none",
      panel.grid.minor = element_blank()
    )
  
  p_pi / p_size + plot_layout(heights = c(1, 1))
}

p_trace <- plot_trace_diagnostics(mcmc_result)
p_trace
```

### 4.2 Convergence Diagnostics (ARI & Accuracy)

```{r plot-convergence, eval=FALSE}
plot_convergence_diagnostics <- function(mcmc_result) {
  burn <- mcmc_result$settings$burn
  keep_idx <- seq(burn + 1, mcmc_result$settings$n_iter)
  
  diagnostics <- data.frame(
    iteration = keep_idx,
    ARI = mcmc_result$ari[keep_idx],
    Accuracy = mcmc_result$acc[keep_idx]
  ) %>%
    pivot_longer(
      cols = c(ARI, Accuracy),
      names_to = "metric",
      values_to = "value"
    )
  
  ggplot(diagnostics, aes(x = iteration, y = value, color = metric)) +
    geom_line(linewidth = 1.2) +
    geom_hline(
      data = diagnostics %>% group_by(metric) %>% summarize(mean_val = mean(value)),
      aes(yintercept = mean_val, color = metric),
      linetype = "dashed",
      linewidth = 1
    ) +
    scale_color_manual(
      name = "Metric",
      values = c("ARI" = "#2C7BB6", "Accuracy" = "#D7191C"),
      labels = c("ARI" = "Adjusted Rand Index", "Accuracy" = "Best Label Accuracy")
    ) +
    labs(
      title = "MCMC Convergence: Clustering Accuracy",
      subtitle = paste("Post burn-in mean ARI:", round(mean(mcmc_result$ari[keep_idx]), 3),
                      "| Mean Accuracy:", round(mean(mcmc_result$acc[keep_idx]), 3)),
      x = "Iteration",
      y = "Value"
    ) +
    theme_minimal() +
    theme(
      legend.position = "bottom",
      panel.grid.minor = element_blank()
    )
}

p_convergence <- plot_convergence_diagnostics(mcmc_result)
p_convergence
```

### 4.3 Posterior Distributions

```{r plot-posterior, eval=FALSE}
plot_posterior_distributions <- function(mcmc_result) {
  burn <- mcmc_result$settings$burn
  keep_idx <- seq(burn + 1, mcmc_result$settings$n_iter)
  K <- mcmc_result$settings$K
  
  ## Posterior of cluster probabilities
  pi_long <- as.data.frame(mcmc_result$pi[keep_idx, ]) %>%
    pivot_longer(
      cols = everything(),
      names_to = "cluster",
      values_to = "value"
    ) %>%
    mutate(cluster = gsub("V", "", cluster))
  
  cluster_colors <- brewer.pal(K, "Set2")
  
  ggplot(pi_long, aes(x = value, fill = cluster)) +
    geom_density(alpha = 0.6, adjust = 1.2) +
    scale_fill_manual(
      name = "Cluster",
      values = cluster_colors,
      labels = paste("Cluster", 1:K)
    ) +
    labs(
      title = "Posterior Distributions: Cluster Probabilities",
      x = "Probability",
      y = "Density"
    ) +
    theme_minimal() +
    theme(
      legend.position = "bottom",
      panel.grid.minor = element_blank()
    )
}

p_posterior <- plot_posterior_distributions(mcmc_result)
p_posterior
```

---

## 5. Estimation Accuracy

### 5.1 Cluster Recovery

```{r plot-cluster-recovery, eval=FALSE}
plot_cluster_recovery <- function(mcmc_result, Z_true, K) {
  burn <- mcmc_result$settings$burn
  keep_idx <- seq(burn + 1, mcmc_result$settings$n_iter)
  
  ## Get posterior mode of Z for each edge
  Z_post <- mcmc_result$Z[keep_idx, ]
  Z_hat <- apply(Z_post, 2, function(x) {
    which.max(tabulate(x, nbins = K))
  })
  
  ## Confusion matrix
  conf_matrix <- table(True = Z_true, Estimated = Z_hat)
  conf_long <- as.data.frame(conf_matrix) %>%
    filter(Freq > 0)
  
  cluster_colors <- brewer.pal(K, "Set2")
  
  ggplot(conf_long, aes(x = Estimated, y = True, fill = Freq)) +
    geom_tile(color = "white", linewidth = 1) +
    geom_text(
      aes(label = Freq),
      size = 6,
      color = "black"
    ) +
    scale_fill_gradientn(
      name = "Count",
      colors = brewer.pal(9, "Blues"),
      na.value = "white"
    ) +
        scale_x_discrete(
      name = "Estimated Cluster",
      labels = paste("Cluster", 1:K)
    ) +
    scale_y_discrete(
      name = "True Cluster",
      labels = paste("Cluster", 1:K)
    ) +
    labs(
      title = "Cluster Recovery: Confusion Matrix",
      subtitle = paste("ARI =", round(adj_rand_index(Z_true, Z_hat), 3)),
      x = "Estimated Cluster",
      y = "True Cluster"
    ) +
    coord_fixed() +
    theme_minimal() +
    theme(
      panel.grid = element_blank(),
      axis.text = element_text(size = 11)
    )
}

p_recovery <- plot_cluster_recovery(mcmc_result, Z_true, K_true)
p_recovery
```

### 5.2 Intensity Estimation

```{r plot-intensity-estimation, eval=FALSE}
plot_intensity_estimation <- function(mcmc_result, Y, Fmat, Z_true, K, theta_true = NULL) {
  burn <- mcmc_result$settings$burn
  keep_idx <- seq(burn + 1, mcmc_result$settings$n_iter)
  
  ## Posterior mean lambda (dimensions: K × TT)
  lambda_mean <- apply(mcmc_result$lambda[keep_idx, , ], c(2, 3), mean)
  
  ## True lambda (compute from theta_true)
  TT <- ncol(Y)
  n_edges <- nrow(Y)
  
  lambda_true <- matrix(0, nrow = n_edges, ncol = TT)
  lambda_est <- matrix(0, nrow = n_edges, ncol = TT)
  
  if (!is.null(theta_true)) {
    ## Compute true lambda for each edge
    for (e in 1:n_edges) {
      k <- Z_true[e]
      eta_e <- rowSums(Fmat * theta_true[k, , ])
      lambda_true[e, ] <- exp(eta_e)
      
      ## Estimated lambda uses the cluster's posterior mean
      lambda_est[e, ] <- lambda_mean[k, ]
    }
  } else {
    ## If theta_true not provided, use posterior mean as proxy
    for (e in 1:n_edges) {
      k <- Z_true[e]
      lambda_est[e, ] <- lambda_mean[k, ]
    }
    lambda_true <- lambda_est
    warning("theta_true not provided. Using posterior mean for comparison.")
  }
  
  ## Compare for a few representative edges
  edge_sample <- sample(1:n_edges, min(6, n_edges))
  
  comparison_data <- data.frame(
    edge = rep(edge_sample, each = TT * 2),
    time = rep(1:TT, length(edge_sample) * 2),
    type = rep(c("True", "Estimated"), each = TT * length(edge_sample)),
    count = c(
      as.vector(lambda_true[edge_sample, ]),
      as.vector(lambda_est[edge_sample, ])
    )
  )
  
  ggplot(comparison_data, aes(x = time, y = count, color = type)) +
    geom_line(linewidth = 0.8) +
    facet_wrap(~ edge, ncol = 3, labeller = labeller(edge = function(x) paste("Edge", x))) +
    scale_color_manual(
      name = "",
      values = c("True" = "#2C7BB6", "Estimated" = "#D7191C"),
      labels = c("True Intensity", "Posterior Mean")
    ) +
    labs(
      title = "Intensity Estimation: True vs Posterior Mean",
      x = "Time Step",
      y = "Intensity (λ)"
    ) +
    theme_minimal() +
    theme(
      legend.position = "bottom",
      panel.grid.minor = element_blank(),
      strip.text = element_text(size = 9)
    )
}
## In your simulation script, after running MCMC:
p_intensity <- plot_intensity_estimation(
  mcmc_result, 
  Y, 
  Fmat, 
  Z_true, 
  K_true,
  theta_true = theta_true  ## Pass the true parameters from data generation
)
p_intensity
```

---

## 6. Combined Visualization

```{r combined-plot, fig.width = 14, fig.height = 12, eval=FALSE}
## Combine all diagnostic plots
(p_network | p_timeseries) /
  (p_trace) /
  (p_convergence | p_recovery) /
  (p_posterior | p_heatmap) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")
```

---

## 7. Summary Statistics

```{r summary-stats, eval=FALSE}
## Print summary
summary(mcmc_result)

## Key metrics
burn <- mcmc_result$settings$burn
keep_idx <- seq(burn + 1, mcmc_result$settings$n_iter)

cat("\n=== Estimation Accuracy ===\n")
cat("Adjusted Rand Index (mean):", round(mean(mcmc_result$ari[keep_idx]), 4), "\n")
cat("Best Label Accuracy (mean):", round(mean(mcmc_result$acc[keep_idx]), 4), "\n")

cat("\n=== Posterior Cluster Probabilities ===\n")
pi_mean <- colMeans(mcmc_result$pi[keep_idx, ])
print(round(pi_mean, 4))

cat("\n=== True Cluster Probabilities ===\n")
print(round(pi_true, 4))

cat("\n=== Computational Performance ===\n")
cat("Total iterations:", mcmc_result$settings$n_iter, "\n")
cat("Burn-in:", mcmc_result$settings$burn, "\n")
cat("Runtime:", round(mcmc_result$settings$total_time, 2), "seconds\n")
cat("Time per iteration:", round(mcmc_result$settings$total_time / mcmc_result$settings$n_iter, 3), "seconds\n")
```

---

## 8. Session Information

```{r session-info}
sessionInfo()
```

---
