# SANDNM simulations

This file contains only the simulation-generation functions for the spatially adaptive neighborhood dynamic network model (SANDNM). Core algorithmic helpers, including `sandnm_season_features()` and `sandnm_baseline_dim()`, are defined in the SANDNM helper block.

```{r sandnm-simulations, send_to = 'R/all-simulations.R'}
#' Construct a directed rectangular grid network for SANDNM simulations.
#'
#' @param nx Number of columns in the rectangular grid.
#' @param ny Number of rows in the rectangular grid.
#'
#' @return A list with node and directed-edge data frames.
sandnm_make_grid_network <- function(nx = 4, ny = 4){
    nodes <- expand.grid(x = seq_len(nx), y = seq_len(ny))
    nodes$node_id <- seq_len(nrow(nodes))

    node_id <- function(x, y){
        return((y - 1) * nx + x)
    }

    edges <- data.frame(from = integer(0), to = integer(0))

    for(y in seq_len(ny)){
        for(x in seq_len(nx)){
            id <- node_id(x, y)

            if(x < nx){
                id2 <- node_id(x + 1, y)
                edges <- rbind(
                    edges,
                    data.frame(from = id, to = id2),
                    data.frame(from = id2, to = id)
                )
            }

            if(y < ny){
                id2 <- node_id(x, y + 1)
                edges <- rbind(
                    edges,
                    data.frame(from = id, to = id2),
                    data.frame(from = id2, to = id)
                )
            }
        }
    }

    edges$edge_id <- seq_len(nrow(edges))

    return(list(nodes = nodes, edges = edges))
}

#' Compute node-to-node Manhattan distances on a rectangular grid.
#'
#' @param nodes Node data frame returned by `sandnm_make_grid_network()`.
#'
#' @return A square distance matrix indexed by node id.
sandnm_make_node_distance <- function(nodes){
    n <- nrow(nodes)
    D <- matrix(0, n, n)

    for(i in seq_len(n)){
        for(j in seq_len(n)){
            D[i, j] <- abs(nodes$x[i] - nodes$x[j]) +
                abs(nodes$y[i] - nodes$y[j])
        }
    }

    return(D)
}

#' Find directed edges incident to a node.
#'
#' @param edges Directed-edge data frame.
#' @param v Node id.
#'
#' @return Integer indices of incident directed edges.
sandnm_incident_edges <- function(edges, v){
    return(which(edges$from == v | edges$to == v))
}

#' Construct edge-wise neighborhood lists.
#'
#' @param edges Directed-edge data frame.
#' @param nodes Node data frame.
#' @param rule Neighborhood rule. Options are `"origin"` and `"two_endpoint"`.
#'
#' @return A list of integer vectors. The `e`th element gives the source edges allowed
#'   to enter the design row for target edge `e`.
sandnm_make_neighbor_list <- function(edges, nodes,
                                      rule = c("origin", "two_endpoint")){
    rule <- match.arg(rule)
    E <- nrow(edges)
    nb <- vector("list", E)

    for(e in seq_len(E)){
        i <- edges$from[e]
        j <- edges$to[e]

        if(rule == "origin"){
            nb_e <- sandnm_incident_edges(edges, i)
        } else {
            nb_e <- union(
                sandnm_incident_edges(edges, i),
                sandnm_incident_edges(edges, j)
            )
        }

        nb[[e]] <- sort(unique(c(e, nb_e)))
    }

    return(nb)
}

#' Construct a target-source edge-pair table from neighborhood lists.
#'
#' @param edges Directed-edge data frame.
#' @param nodes Node data frame.
#' @param nb_list Edge-wise neighborhood list.
#' @param label Prefix used for pair names.
#'
#' @return A data frame containing target edge, source edge, relation type, distance,
#'   and a unique pair name.
sandnm_make_pair_table <- function(edges, nodes, nb_list, label = "M"){
    node_D <- sandnm_make_node_distance(nodes)
    out <- vector("list", length(nb_list))
    kk <- 0

    for(e in seq_along(nb_list)){
        target_from <- edges$from[e]
        target_to <- edges$to[e]
        srcs <- nb_list[[e]]

        for(u in srcs){
            kk <- kk + 1
            source_from <- edges$from[u]
            source_to <- edges$to[u]

            relation <- if(u == e){
                "self"
            } else if(source_from == target_from || source_to == target_from){
                "origin"
            } else if(source_from == target_to || source_to == target_to){
                "destination"
            } else {
                "nearby"
            }

            d1 <- node_D[target_from, source_from]
            d2 <- node_D[target_from, source_to]
            d3 <- node_D[target_to, source_from]
            d4 <- node_D[target_to, source_to]
            dist_eu <- min(d1, d2, d3, d4)

            out[[kk]] <- data.frame(
                target = e,
                source = u,
                relation = relation,
                distance = dist_eu,
                pair_name = paste0(label, "_e", e, "_lag", u),
                stringsAsFactors = FALSE
            )
        }
    }

    ret <- do.call(rbind, out)
    rownames(ret) <- NULL

    return(ret)
}

#' Simulate SANDNM count data on a directed network.
#'
#' The default data-generating process uses an origin-centered local propagation
#' structure with daily Fourier seasonality.
#'
#' @param net Network list returned by `sandnm_make_grid_network()`.
#' @param nb_true True neighborhood list used in the data-generating process.
#' @param T_full Total number of time points.
#' @param steps_day Number of time points per day.
#' @param harmonics Number of Fourier harmonics.
#' @param center Centering constant for transformed lagged counts.
#' @param scale_x Scaling constant for transformed lagged counts.
#' @param base_intercept Baseline log-intensity.
#' @param seasonal_coef Named vector of Fourier coefficients.
#' @param theta_sd Innovation standard deviation for active propagation coefficients.
#' @param seed Optional random seed.
#'
#' @return A list containing simulated counts, true intensities, true states, and
#'   the true edge-pair table.
sandnm_simulate_adaptive_counts <- function(net, nb_true, T_full = 14 * 48,
                                            steps_day = 48, harmonics = 2,
                                            center = log(8), scale_x = 1.5,
                                            base_intercept = log(6.5),
                                            seasonal_coef = c(sin1 = -0.26,
                                                              cos1 = -0.30,
                                                              sin2 = -0.18,
                                                              cos2 = -0.28),
                                            theta_sd = 0.0015,
                                            seed = NULL){
    if(!is.null(seed)) set.seed(seed)

    edges <- net$edges
    nodes <- net$nodes
    E <- nrow(edges)

    pair_true <- sandnm_make_pair_table(edges, nodes, nb_true, label = "true")
    P <- nrow(pair_true)

    theta0_pairs <- numeric(P)
    true_active <- logical(P)

    for(l in seq_len(P)){
        rel <- pair_true$relation[l]
        d <- pair_true$distance[l]

        if(rel == "self"){
            theta0_pairs[l] <- rnorm(1, mean = 0.48, sd = 0.05)
            true_active[l] <- TRUE
        } else if(rel == "origin"){
            theta0_pairs[l] <- rnorm(1, mean = 0.20, sd = 0.04) *
                exp(-0.15 * (d - 1))
            true_active[l] <- TRUE
        } else {
            theta0_pairs[l] <- 0
            true_active[l] <- FALSE
        }
    }

    pair_true$true_active <- true_active

    B <- sandnm_baseline_dim(harmonics)
    season_names <- names(sandnm_season_features(1, steps_day, harmonics))
    theta_true <- matrix(0, nrow = T_full, ncol = B + P)
    colnames(theta_true) <- c("intercept", season_names, pair_true$pair_name)

    theta_true[1, 1] <- base_intercept

    if(B > 1){
        sname <- colnames(theta_true)[2:B]
        season_init <- seasonal_coef[sname]
        season_init[is.na(season_init)] <- 0
        theta_true[1, 2:B] <- season_init
    }

    theta_true[1, B + seq_len(P)] <- theta0_pairs

    state_sd <- c(0.0015, rep(0.0005, B - 1), rep(theta_sd, P))

    for(tt in 2:T_full){
        theta_true[tt, ] <- theta_true[tt - 1, ] + rnorm(B + P, 0, state_sd)
        theta_true[tt, B + which(!true_active)] <- 0
    }

    Y <- matrix(0, nrow = T_full, ncol = E)
    Lambda <- matrix(NA_real_, nrow = T_full, ncol = E)
    y0 <- rpois(E, lambda = exp(base_intercept))

    for(tt in seq_len(T_full)){
        y_lag <- if(tt == 1) y0 else Y[tt - 1, ]
        sfeat <- sandnm_season_features(tt, steps_day, harmonics)
        x_lag <- (log1p(y_lag) - center) / scale_x

        eta <- rep(theta_true[tt, 1], E)

        if(B > 1){
            eta <- eta + sum(theta_true[tt, 2:B] * sfeat)
        }

        for(l in seq_len(P)){
            eta[pair_true$target[l]] <- eta[pair_true$target[l]] +
                theta_true[tt, B + l] * x_lag[pair_true$source[l]]
        }

        eta <- pmin(pmax(eta, -8), 8)
        Lambda[tt, ] <- exp(eta)
        Y[tt, ] <- rpois(E, Lambda[tt, ])
    }

    colnames(Y) <- paste0("e", seq_len(E))
    colnames(Lambda) <- paste0("e", seq_len(E))

    return(list(
        Y = Y,
        y0 = y0,
        Lambda_true = Lambda,
        theta_true = theta_true,
        pair_table_true = pair_true,
        edges = edges,
        nodes = nodes
    ))
}

#' Expand true active/inactive labels to a broader candidate pair table.
#'
#' Pairs not included in the true data-generating neighborhood are marked inactive.
#'
#' @param pair_broad Broad candidate pair table.
#' @param pair_true True pair table returned by `sandnm_simulate_adaptive_counts()`.
#'
#' @return A copy of `pair_broad` with a logical `true_active` column.
sandnm_make_true_pair_broad <- function(pair_broad, pair_true){
    key_true <- paste(pair_true$target, pair_true$source, sep = "_")
    key_broad <- paste(pair_broad$target, pair_broad$source, sep = "_")
    idx <- match(key_broad, key_true)

    out <- pair_broad
    out$true_active <- ifelse(is.na(idx), FALSE, pair_true$true_active[idx])

    return(out)
}

#' Prepare a complete SANDNM simulation object.
#'
#' This convenience wrapper generates a grid network, origin-centered and two-endpoint
#' neighborhood rules, simulated counts, train/test splits, and a broad-neighborhood
#' truth table for evaluating shrinkage.
#'
#' @param nx Number of grid columns.
#' @param ny Number of grid rows.
#' @param steps_day Number of time points per day.
#' @param n_days Number of simulated days.
#' @param n_train_days Number of training days.
#' @param harmonics Number of Fourier harmonics.
#' @param seed Random seed.
#'
#' @return A list containing the simulated data, network objects, candidate pair
#'   tables, train/test splits, and common PG dispersion value.
sandnm_prepare_simulation <- function(nx = 4, ny = 4, steps_day = 48,
                                      n_days = 14, n_train_days = 10,
                                      harmonics = 2, seed = 20260509){
    net <- sandnm_make_grid_network(nx, ny)

    nb_origin <- sandnm_make_neighbor_list(net$edges, net$nodes, rule = "origin")
    nb_two <- sandnm_make_neighbor_list(net$edges, net$nodes, rule = "two_endpoint")

    pair_origin <- sandnm_make_pair_table(net$edges, net$nodes, nb_origin,
                                          label = "origin")
    pair_two <- sandnm_make_pair_table(net$edges, net$nodes, nb_two,
                                       label = "two")
    pair_broad <- sandnm_make_pair_table(net$edges, net$nodes, nb_two,
                                         label = "broad")

    T_full <- n_days * steps_day
    T_train <- n_train_days * steps_day

    sim <- sandnm_simulate_adaptive_counts(
        net = net,
        nb_true = nb_origin,
        T_full = T_full,
        steps_day = steps_day,
        harmonics = harmonics,
        seed = seed
    )

    true_pair_broad <- sandnm_make_true_pair_broad(pair_broad,
                                                   sim$pair_table_true)

    Y <- sim$Y
    Lambda <- sim$Lambda_true
    Y_train <- Y[seq_len(T_train), , drop = FALSE]
    Lambda_train <- Lambda[seq_len(T_train), , drop = FALSE]
    Y_test <- Y[(T_train + 1):T_full, , drop = FALSE]
    Lambda_test <- Lambda[(T_train + 1):T_full, , drop = FALSE]
    max_train_count <- max(Y_train)

    return(list(
        net = net,
        sim = sim,
        nb_origin = nb_origin,
        nb_two = nb_two,
        pair_origin = pair_origin,
        pair_two = pair_two,
        pair_broad = pair_broad,
        true_pair_broad = true_pair_broad,
        steps_day = steps_day,
        harmonics = harmonics,
        T_full = T_full,
        T_train = T_train,
        H_test = T_full - T_train,
        Y_train = Y_train,
        Y_test = Y_test,
        Lambda_train = Lambda_train,
        Lambda_test = Lambda_test,
        y_last_train = Y[T_train, ],
        r_pg_common = ceiling((max_train_count + 2 * sqrt(max_train_count)) * 50)
    ))
}
```

# SANDNM visualization helpers

These functions provide lightweight plotting utilities for SANDNM simulation studies. They are optional diagnostics and depend on `ggplot2`.

```{r sandnm-visualizations, send_to = 'R/all-simulations.R'}
#' Convert simulated SANDNM counts into a total-flow time-series data frame.
#'
#' @param Y Count matrix with rows as time points and columns as directed edges.
#' @param Lambda_true Optional true intensity matrix with the same dimension as `Y`.
#' @param T_train Optional training-period length. If supplied, a `split` column is added.
#' @param steps_day Number of time points per day.
#'
#' @return A data frame with total counts and, if supplied, total intensities.
sandnm_total_flow_df <- function(Y, Lambda_true = NULL, T_train = NULL,
                                 steps_day = 48){
    T_full <- nrow(Y)

    out <- data.frame(
        t = seq_len(T_full),
        day = (seq_len(T_full) - 1) / steps_day,
        hour = ((seq_len(T_full) - 1) %% steps_day) / 2,
        total_flow = rowSums(Y),
        stringsAsFactors = FALSE
    )

    if(!is.null(Lambda_true)){
        out$total_lambda <- rowSums(Lambda_true)
    }

    if(!is.null(T_train)){
        out$split <- ifelse(out$t <= T_train, "training", "test")
    }

    return(out)
}

#' Plot total network flow for a SANDNM simulation.
#'
#' @param Y Count matrix.
#' @param Lambda_true Optional true intensity matrix.
#' @param T_train Optional training-period length.
#' @param steps_day Number of time points per day.
#' @param title Optional plot title.
#'
#' @return A ggplot object.
sandnm_plot_total_flow <- function(Y, Lambda_true = NULL, T_train = NULL,
                                   steps_day = 48,
                                   title = "Simulated total network flow"){
    df <- sandnm_total_flow_df(Y, Lambda_true, T_train, steps_day)

    p <- ggplot2::ggplot(df, ggplot2::aes(x = day)) +
        ggplot2::geom_line(
            ggplot2::aes(y = total_flow),
            colour = "#2166AC",
            linewidth = 0.45,
            alpha = 0.75
        ) +
        ggplot2::labs(
            x = "Day",
            y = "Total network flow",
            title = title
        ) +
        ggplot2::theme_bw() +
        ggplot2::theme(
            panel.grid.minor = ggplot2::element_blank(),
            plot.title = ggplot2::element_text(face = "bold")
        )

    if(!is.null(Lambda_true)){
        p <- p + ggplot2::geom_line(
            ggplot2::aes(y = total_lambda),
            colour = "#E66101",
            linetype = "dashed",
            linewidth = 0.75
        )
    }

    if(!is.null(T_train)){
        p <- p + ggplot2::geom_vline(
            xintercept = T_train / steps_day,
            colour = "grey35",
            linetype = "dotted",
            linewidth = 0.65
        )
    }

    return(p)
}

#' Plot average daily total-flow profiles for a SANDNM simulation.
#'
#' @param Y Count matrix.
#' @param Lambda_true Optional true intensity matrix.
#' @param T_train Optional training-period length. If supplied, training and test profiles are faceted.
#' @param steps_day Number of time points per day.
#' @param title Optional plot title.
#'
#' @return A ggplot object.
sandnm_plot_daily_profile <- function(Y, Lambda_true = NULL, T_train = NULL,
                                      steps_day = 48,
                                      title = "Average daily profile"){
    df <- sandnm_total_flow_df(Y, Lambda_true, T_train, steps_day)

    if(is.null(T_train)){
        df$split <- "all"
    }

    sp <- split(df, list(df$split, df$hour), drop = TRUE)
    daily <- do.call(rbind, lapply(sp, function(z){
        data.frame(
            split = z$split[1],
            hour = z$hour[1],
            mean_total = mean(z$total_flow),
            p10 = stats::quantile(z$total_flow, 0.10),
            p90 = stats::quantile(z$total_flow, 0.90),
            mean_lambda = if("total_lambda" %in% names(z)) mean(z$total_lambda) else NA_real_,
            stringsAsFactors = FALSE
        )
    }))
    rownames(daily) <- NULL

    p <- ggplot2::ggplot(daily, ggplot2::aes(x = hour)) +
        ggplot2::geom_ribbon(
            ggplot2::aes(ymin = p10, ymax = p90),
            fill = "#BFD3E6",
            alpha = 0.40
        ) +
        ggplot2::geom_line(
            ggplot2::aes(y = mean_total),
            colour = "#2166AC",
            linewidth = 0.95
        ) +
        ggplot2::labs(
            x = "Hour of day",
            y = "Average total flow",
            title = title
        ) +
        ggplot2::theme_bw() +
        ggplot2::theme(
            panel.grid.minor = ggplot2::element_blank(),
            plot.title = ggplot2::element_text(face = "bold"),
            strip.background = ggplot2::element_rect(fill = "grey92", colour = "grey70"),
            strip.text = ggplot2::element_text(face = "bold")
        )

    if(!all(is.na(daily$mean_lambda))){
        p <- p + ggplot2::geom_line(
            ggplot2::aes(y = mean_lambda),
            colour = "#E66101",
            linetype = "dashed",
            linewidth = 0.75
        )
    }

    if(length(unique(daily$split)) > 1){
        p <- p + ggplot2::facet_wrap(~ split)
    }

    return(p)
}

#' Plot an edge-level count heatmap.
#'
#' @param Y Count matrix.
#' @param steps_day Number of time points per day.
#' @param first_days Number of initial days to plot. If `NULL`, all days are plotted.
#' @param title Optional plot title.
#'
#' @return A ggplot object.
sandnm_plot_edge_heatmap <- function(Y, steps_day = 48, first_days = 5,
                                     title = "Edge-level count heatmap"){
    T_full <- nrow(Y)
    E <- ncol(Y)
    keep <- seq_len(T_full)

    if(!is.null(first_days)){
        keep <- keep[(keep - 1) / steps_day < first_days]
    }

    mat <- Y[keep, , drop = FALSE]
    colnames(mat) <- paste0("e", seq_len(E))
    df <- as.data.frame(as.table(mat), stringsAsFactors = FALSE)
    names(df) <- c("time_id", "edge", "count")
    df$t <- as.integer(df$time_id)
    df$day <- (keep[df$t] - 1) / steps_day
    df$edge_id <- as.integer(sub("e", "", df$edge))
    df$edge_label <- factor(df$edge_id, levels = rev(seq_len(E)))

    p <- ggplot2::ggplot(df, ggplot2::aes(x = day, y = edge_label, fill = count)) +
        ggplot2::geom_tile() +
        ggplot2::scale_fill_gradientn(
            colours = c("#2166AC", "#67A9CF", "#F7F7F7", "#FDB863", "#E66101"),
            trans = "sqrt",
            name = "Count"
        ) +
        ggplot2::labs(
            x = "Day",
            y = "Directed edge index",
            title = title
        ) +
        ggplot2::theme_bw() +
        ggplot2::theme(
            panel.grid = ggplot2::element_blank(),
            plot.title = ggplot2::element_text(face = "bold"),
            legend.position = "right",
            axis.text.y = ggplot2::element_text(size = 5)
        )

    return(p)
}

#' Construct edge-plot coordinates for network snapshots.
#'
#' @param edges Directed-edge data frame.
#' @param nodes Node data frame.
#' @param value Numeric vector of edge values.
#'
#' @return A data frame used by `sandnm_plot_network_snapshot()`.
sandnm_make_edge_plot_data <- function(edges, nodes, value){
    edge_df <- edges
    edge_df$value <- as.numeric(value)
    edge_df$x0 <- nodes$x[edge_df$from]
    edge_df$y0 <- nodes$y[edge_df$from]
    edge_df$x1 <- nodes$x[edge_df$to]
    edge_df$y1 <- nodes$y[edge_df$to]

    dx <- edge_df$x1 - edge_df$x0
    dy <- edge_df$y1 - edge_df$y0
    len <- sqrt(dx^2 + dy^2)
    len[len == 0] <- 1

    offset <- 0.06
    edge_df$x0 <- edge_df$x0 + offset * (-dy / len)
    edge_df$y0 <- edge_df$y0 + offset * ( dx / len)
    edge_df$x1 <- edge_df$x1 + offset * (-dy / len)
    edge_df$y1 <- edge_df$y1 + offset * ( dx / len)
    edge_df$edge_lab_x <- (edge_df$x0 + edge_df$x1) / 2
    edge_df$edge_lab_y <- (edge_df$y0 + edge_df$y1) / 2

    return(edge_df)
}

#' Plot a network snapshot for generated edge counts or intensities.
#'
#' @param value Numeric vector of edge values.
#' @param edges Directed-edge data frame.
#' @param nodes Node data frame.
#' @param title Optional plot title. Use `NULL` to suppress title.
#' @param value_name Legend title.
#' @param show_edge_id Whether to display edge ids.
#' @param limits Optional common limits for color and line width scales.
#'
#' @return A ggplot object.
sandnm_plot_network_snapshot <- function(value, edges, nodes, title = NULL,
                                         value_name = "Count",
                                         show_edge_id = FALSE,
                                         limits = NULL){
    edge_df <- sandnm_make_edge_plot_data(edges, nodes, value)

    p <- ggplot2::ggplot() +
        ggplot2::geom_segment(
            data = edge_df,
            ggplot2::aes(x = x0, y = y0, xend = x1, yend = y1,
                         linewidth = value, colour = value),
            alpha = 0.95,
            lineend = "round",
            arrow = grid::arrow(length = grid::unit(0.10, "inches"), type = "closed")
        ) +
        ggplot2::geom_point(data = nodes, ggplot2::aes(x = x, y = y),
                            size = 3, colour = "black") +
        ggplot2::geom_text(data = nodes, ggplot2::aes(x = x, y = y, label = node_id),
                           vjust = -1.0, size = 3.2) +
        ggplot2::scale_linewidth_continuous(
            name = value_name,
            range = c(0.45, 2.8),
            limits = limits
        ) +
        ggplot2::scale_colour_gradientn(
            colours = c("#2166AC", "#4393C3", "#92C5DE", "#FDD49E", "#FDB863", "#E66101"),
            trans = "sqrt",
            limits = limits,
            name = value_name
        ) +
        ggplot2::coord_equal() +
        ggplot2::labs(title = title, x = NULL, y = NULL) +
        ggplot2::theme_bw() +
        ggplot2::theme(
            axis.text = ggplot2::element_blank(),
            axis.ticks = ggplot2::element_blank(),
            panel.grid = ggplot2::element_blank(),
            panel.background = ggplot2::element_rect(fill = "grey96", colour = NA),
            plot.title = ggplot2::element_text(face = "bold"),
            legend.position = "right"
        )

    if(show_edge_id){
        p <- p + ggplot2::geom_text(
            data = edge_df,
            ggplot2::aes(x = edge_lab_x, y = edge_lab_y, label = edge_id),
            size = 2.4,
            colour = "black",
            check_overlap = TRUE
        )
    }

    return(p)
}

#' Make a data frame for held-out total-flow forecasts.
#'
#' @param fc Forecast object returned by `sandnm_forecast_recursive_blocks()`.
#' @param Y_test Held-out count matrix.
#' @param Lambda_test Held-out true intensity matrix.
#' @param T_train Training-period length.
#' @param steps_day Number of time points per day.
#'
#' @return A data frame for plotting.
sandnm_forecast_total_df <- function(fc, Y_test, Lambda_test, T_train,
                                     steps_day = 48){
    H <- nrow(fc$lambda_mean)

    return(data.frame(
        h = seq_len(H),
        day = (T_train + seq_len(H)) / steps_day,
        forecast_day = seq_len(H) / steps_day,
        method = fc$label,
        observed = as.numeric(rowSums(Y_test[seq_len(H), , drop = FALSE])),
        truth = as.numeric(rowSums(Lambda_test[seq_len(H), , drop = FALSE])),
        predicted = as.numeric(rowSums(fc$lambda_mean)),
        lower = as.numeric(rowSums(fc$lambda_lower)),
        upper = as.numeric(rowSums(fc$lambda_upper)),
        stringsAsFactors = FALSE
    ))
}

#' Plot held-out recursive forecasts of total network flow.
#'
#' @param fc_list A list of forecast objects.
#' @param Y_test Held-out count matrix.
#' @param Lambda_test Held-out true intensity matrix.
#' @param T_train Training-period length.
#' @param steps_day Number of time points per day.
#' @param title Optional plot title.
#'
#' @return A ggplot object.
sandnm_plot_forecast_total <- function(fc_list, Y_test, Lambda_test, T_train,
                                       steps_day = 48,
                                       title = "Held-out recursive forecast of total network flow"){
    if(!is.list(fc_list) || is.null(fc_list[[1]]$lambda_mean)){
        fc_list <- list(fc_list)
    }

    df <- do.call(rbind, lapply(fc_list, sandnm_forecast_total_df,
                                Y_test = Y_test,
                                Lambda_test = Lambda_test,
                                T_train = T_train,
                                steps_day = steps_day))

    p <- ggplot2::ggplot(df, ggplot2::aes(x = forecast_day)) +
        ggplot2::geom_ribbon(
            ggplot2::aes(ymin = lower, ymax = upper),
            fill = "#BFD3E6",
            alpha = 0.35
        ) +
        ggplot2::geom_line(
            ggplot2::aes(y = observed),
            colour = "#2166AC",
            linewidth = 0.45,
            alpha = 0.75
        ) +
        ggplot2::geom_line(
            ggplot2::aes(y = predicted),
            colour = "#E66101",
            linewidth = 0.85
        ) +
        ggplot2::geom_line(
            ggplot2::aes(y = truth),
            colour = "grey25",
            linetype = "dashed",
            linewidth = 0.65
        ) +
        ggplot2::facet_wrap(~ method, ncol = 1) +
        ggplot2::labs(x = "Forecast day", y = "Total network flow", title = title) +
        ggplot2::theme_bw() +
        ggplot2::theme(
            panel.grid.minor = ggplot2::element_blank(),
            plot.title = ggplot2::element_text(face = "bold"),
            strip.background = ggplot2::element_rect(fill = "grey92", colour = "grey70"),
            strip.text = ggplot2::element_text(face = "bold")
        )

    return(p)
}

#' Plot held-out recursive forecasts for one directed edge.
#'
#' @param fc_list A list of forecast objects.
#' @param edge_id Directed edge id.
#' @param Y_test Held-out count matrix.
#' @param Lambda_test Held-out true intensity matrix.
#' @param T_train Training-period length.
#' @param steps_day Number of time points per day.
#'
#' @return A ggplot object.
sandnm_plot_forecast_edge <- function(fc_list, edge_id, Y_test, Lambda_test,
                                      T_train, steps_day = 48){
    if(!is.list(fc_list) || is.null(fc_list[[1]]$lambda_mean)){
        fc_list <- list(fc_list)
    }

    one_df <- function(fc){
        H <- nrow(fc$lambda_mean)
        data.frame(
            h = seq_len(H),
            forecast_day = seq_len(H) / steps_day,
            method = fc$label,
            observed = Y_test[seq_len(H), edge_id],
            truth = Lambda_test[seq_len(H), edge_id],
            mean = fc$lambda_mean[, edge_id],
            lower = fc$lambda_lower[, edge_id],
            upper = fc$lambda_upper[, edge_id],
            stringsAsFactors = FALSE
        )
    }

    df <- do.call(rbind, lapply(fc_list, one_df))

    p <- ggplot2::ggplot(df, ggplot2::aes(x = forecast_day)) +
        ggplot2::geom_ribbon(
            ggplot2::aes(ymin = lower, ymax = upper),
            fill = "#BFD3E6",
            alpha = 0.40
        ) +
        ggplot2::geom_line(
            ggplot2::aes(y = mean),
            colour = "#E66101",
            linewidth = 0.90
        ) +
        ggplot2::geom_point(
            ggplot2::aes(y = observed),
            colour = "#2166AC",
            size = 0.75,
            alpha = 0.55
        ) +
        ggplot2::geom_line(
            ggplot2::aes(y = truth),
            colour = "grey25",
            linetype = "dashed",
            linewidth = 0.65
        ) +
        ggplot2::facet_wrap(~ method, ncol = 1) +
        ggplot2::labs(
            x = "Forecast day",
            y = paste0("Flow on edge ", edge_id),
            title = paste0("Held-out recursive forecast for directed Edge ", edge_id)
        ) +
        ggplot2::theme_bw() +
        ggplot2::theme(
            panel.grid.minor = ggplot2::element_blank(),
            plot.title = ggplot2::element_text(face = "bold"),
            strip.background = ggplot2::element_rect(fill = "grey92", colour = "grey70"),
            strip.text = ggplot2::element_text(face = "bold")
        )

    return(p)
}

#' Plot test-period edge-level intensity forecast error heatmaps.
#'
#' @param fc_list A list of forecast objects.
#' @param Lambda_test Held-out true intensity matrix.
#' @param steps_day Number of time points per day.
#'
#' @return A ggplot object.
sandnm_plot_forecast_error_heatmap <- function(fc_list, Lambda_test,
                                               steps_day = 48){
    if(!is.list(fc_list) || is.null(fc_list[[1]]$lambda_mean)){
        fc_list <- list(fc_list)
    }

    one_df <- function(fc){
        H <- nrow(fc$lambda_mean)
        E <- ncol(fc$lambda_mean)
        err_mat <- abs(fc$lambda_mean - Lambda_test[seq_len(H), , drop = FALSE])
        colnames(err_mat) <- paste0("e", seq_len(E))
        df <- as.data.frame(as.table(err_mat), stringsAsFactors = FALSE)
        names(df) <- c("time_id", "edge", "abs_error")
        df$h <- as.integer(df$time_id)
        df$forecast_day <- (df$h - 1) / steps_day
        df$edge_id <- as.integer(sub("e", "", df$edge))
        df$edge_label <- factor(df$edge_id, levels = rev(seq_len(E)))
        df$method <- fc$label
        return(df)
    }

    df <- do.call(rbind, lapply(fc_list, one_df))

    p <- ggplot2::ggplot(df, ggplot2::aes(x = forecast_day, y = edge_label,
                                          fill = abs_error)) +
        ggplot2::geom_tile() +
        ggplot2::facet_wrap(~ method, ncol = 1) +
        ggplot2::scale_fill_gradientn(
            colours = c("#2166AC", "#67A9CF", "#F7F7F7", "#FDB863", "#E66101"),
            trans = "sqrt",
            name = "Abs. error"
        ) +
        ggplot2::labs(
            x = "Forecast day",
            y = "Directed edge index",
            title = "Test-period edge-level forecast error heatmap"
        ) +
        ggplot2::theme_bw() +
        ggplot2::theme(
            panel.grid = ggplot2::element_blank(),
            plot.title = ggplot2::element_text(face = "bold"),
            strip.background = ggplot2::element_rect(fill = "grey92", colour = "grey70"),
            strip.text = ggplot2::element_text(face = "bold"),
            axis.text.y = ggplot2::element_text(size = 5)
        )

    return(p)
}

#' Plot shrinkage-scale summaries by relation and edge-pair distance.
#'
#' @param shrink_sum Output of `sandnm_shrinkage_pair_summary_blocks()`.
#' @param threshold Optional selection threshold shown as a dashed horizontal line.
#'
#' @return A ggplot object.
sandnm_plot_shrinkage_summary <- function(shrink_sum, threshold = 0.03){
    relation_cols <- c(
        self = "#2166AC",
        origin = "#FDB863",
        destination = "#BFD3E6",
        nearby = "grey60"
    )

    p <- ggplot2::ggplot(shrink_sum,
                         ggplot2::aes(x = distance, y = lambda_mean,
                                      colour = relation)) +
        ggplot2::geom_point(ggplot2::aes(shape = true_active),
                            alpha = 0.75, size = 1.8) +
        ggplot2::scale_colour_manual(values = relation_cols, drop = FALSE) +
        ggplot2::scale_shape_manual(values = c(`FALSE` = 1, `TRUE` = 16),
                                    labels = c("Inactive", "Active")) +
        ggplot2::labs(
            x = "Edge-pair distance",
            y = expression(posterior~mean~lambda[e,u]),
            colour = "Relation",
            shape = "True status",
            title = "Distance-regularized shrinkage scales"
        ) +
        ggplot2::theme_bw() +
        ggplot2::theme(
            panel.grid.minor = ggplot2::element_blank(),
            plot.title = ggplot2::element_text(face = "bold")
        )

    if(!is.null(threshold)){
        p <- p + ggplot2::geom_hline(
            yintercept = threshold,
            colour = "grey35",
            linetype = "dashed",
            linewidth = 0.55
        )
    }

    return(p)
}
```
