---
title: "Developing bdynets"
author: "Sheng Jiang"
output: rmarkdown::html_document
---

# One modular package

The maintained R package is in `bdynets/`. Edit `bdynets/R/*.R` directly.
This document explains development; rendering it does not generate or alter
package code. The former litr setup is retained in
`docs/legacy-litr/index.Rmd.txt` for historical reference.

# Install

```{r install, eval=FALSE}
pak::pak("sj156/bdynets/bdynets", dependencies = TRUE)
library(bdynets)
```

# Develop and verify

From the repository root, generate help and NAMESPACE from R source comments,
then run the module tests:

```{r develop, eval=FALSE}
roxygen2::roxygenise("bdynets")
testthat::test_local("bdynets")
```

Build and check from the shell:

```sh
R CMD build bdynets
R CMD check --no-manual bdynets_0.1.0.tar.gz
```

# Modules

Graph-informed Gaussian/static mixtures use the `gmde_*` entry points.
The historical `gibbs_sampler()` remains available as a separate experimental
count-mixture engine. The newer module does not call its approximate PG or
jittered covariance helpers. See `bdynets/README.md` for a complete example.

The remaining root R Markdown chapters retain mathematical explanations and
old experiments. They are reference material, not the package build inputs.
