---
title: "data_process"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## 1.Initial Data
*variables used in the map are in blue*

This folder uses PeMS Station 5-Minute data for the Los Angeles area. The date range is April 2026. The districts are D7, D8, and D12.

```text
PeMS_LA_2026_H1_speed/
├── code/
├── code_5min/
├── data/
│   ├── April/
│   └── raw/
├── map/
├── processed/
└── data_process.Rmd
```

```{r}
list.files(".", recursive = TRUE)
```

### 1.1 *Station Metadata*

Metadata gives the location and road attributes for each station. Station 5-Minute files use station IDs, so metadata is needed before drawing the map.

The metadata files are stored in `data/raw/`.

```{r}
metadata_files <- list.files("data/raw", pattern = "text_meta", full.names = TRUE)
basename(metadata_files)
```

The fields used from metadata are:

* <span style="color: blue;">**station**</span>: PeMS station ID.

* <span style="color: blue;">**latitude**</span>: Station latitude.

* <span style="color: blue;">**longitude**</span>: Station longitude.

* <span style="color: blue;">**freeway**</span>: Freeway or route number.

* <span style="color: blue;">**direction**</span>: Travel direction.

* <span style="color: blue;">**abs_pm**</span>: Absolute postmile. This is used to order stations along the same freeway and direction.

* <span style="color: blue;">**type**</span>: Station type. This script keeps `ML`, which means mainline.

* **name**: Station name or nearby road name.

```{r}
if (length(metadata_files) > 0) {
  read.delim(metadata_files[1], nrows = 10, check.names = FALSE)
}
```

### 1.2 *Station 5-Minute*

Station 5-Minute contains one row per station and 5-minute interval. The April files are stored by district:

```text
data/April/D07/
data/April/D08/
data/April/D12/
```

```{r}
five_min_files <- list.files("data/April", pattern = "text_station_5min_2026_04", recursive = TRUE, full.names = TRUE)
length(five_min_files)
head(basename(five_min_files))
tail(basename(five_min_files))
```

The fields used from Station 5-Minute are:

* <span style="color: blue;">**timestamp**</span>: Beginning time of the 5-minute interval.

* <span style="color: blue;">**station**</span>: PeMS station ID.

* <span style="color: blue;">**district**</span>: Caltrans district number.

* <span style="color: blue;">**freeway**</span>: Freeway or route number.

* <span style="color: blue;">**direction**</span>: Travel direction.

* <span style="color: blue;">**lane_type**</span>: Station category. The script keeps `ML`.

* <span style="color: blue;">**average_speed**</span>: Average speed for the station and 5-minute interval, in mph.

The raw files also include flow, occupancy, and lane-level columns. They are not used in this speed map.

```{r}
five_min_columns <- c(
  "timestamp", "station", "district", "freeway", "direction", "lane_type",
  "station_length", "samples", "percentage_observed", "total_flow",
  "average_occupancy", "average_speed"
)

for (lane in 1:8) {
  five_min_columns <- c(
    five_min_columns,
    paste0("lane", lane, "_samples"),
    paste0("lane", lane, "_flow"),
    paste0("lane", lane, "_average_occupancy"),
    paste0("lane", lane, "_average_speed"),
    paste0("lane", lane, "_observed")
  )
}

if (length(five_min_files) > 0) {
  preview <- read.csv(
    five_min_files[1],
    nrows = 10,
    header = FALSE,
    col.names = five_min_columns,
    check.names = FALSE
  )
  preview[, c("timestamp", "station", "district", "freeway", "direction", "lane_type", "average_speed")]
}
```

## 2.Main Code

The April 5-minute map is generated by:

```text
code_5min/build_la_2026_april_5min_speed_map.py
```

Run it from this folder:

```{python eval=FALSE}
python3 code_5min/build_la_2026_april_5min_speed_map.py
```

The script:

1. reads metadata from `data/raw/`;
2. reads the April Station 5-Minute files from `data/April/`;
3. keeps mainline stations (`ML`);
4. keeps speed values between 1 and 100 mph;
5. creates a 5-minute time index from `2026-04-01 00:00` to `2026-04-30 23:55`;
6. groups stations by district, freeway, and direction;
7. orders stations by absolute postmile;
8. connects nearby neighboring stations as road links;
9. assigns each segment the average speed of its two endpoint stations;
10. writes the processed files and HTML map.

OpenStreetMap is used as the basemap. The colored road links are built from PeMS station locations.

## 3.Processed Outputs

```{r}
processed_files <- list.files("processed", pattern = "2026_04_5min", full.names = TRUE)
file.info(processed_files)[, c("size", "mtime")]
```

### 3.1 *la_area_stations_2026_04_5min.csv*

Station locations used in the map.

```{r}
stations_path <- "processed/la_area_stations_2026_04_5min.csv"
if (file.exists(stations_path)) {
  stations <- read.csv(stations_path)
  head(stations, 10)
}
```

### 3.2 *la_area_speed_links_2026_04_5min.csv*

Station-to-station road links used as colored line features.

```{r}
links_path <- "processed/la_area_speed_links_2026_04_5min.csv"
if (file.exists(links_path)) {
  links <- read.csv(links_path)
  head(links, 10)
}
```

### 3.3 *la_area_freeway_speeds_2026_04_5min_summary.csv*

One row per 5-minute interval. It stores the number of road links with speed values, mean speed, and median speed.

```{r}
summary_path <- "processed/la_area_freeway_speeds_2026_04_5min_summary.csv"
if (file.exists(summary_path)) {
  speed_summary <- read.csv(summary_path)
  head(speed_summary, 10)
  tail(speed_summary, 10)
}
```

### 3.4 *la_area_freeway_speeds_2026_04_5min.json*

The JSON file is embedded into the HTML map. It contains the time labels, stations, segment coordinates, and 5-minute speed values.

```{r}
json_path <- "processed/la_area_freeway_speeds_2026_04_5min.json"
if (file.exists(json_path)) {
  file.info(json_path)[, c("size", "mtime")]
}
```

## 4.Output Map

The HTML map is:

```{r}
map_files <- list.files("map", pattern = "2026_04_5min.*\\.html$", full.names = TRUE)
map_files
```

The map includes an April 2026 5-minute time slider, play/reset controls, speed-colored freeway road links, optional station points, optional road casing, and a lower-left speed legend with the current time and summary numbers.
