---
title: "data_process"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## 1.Initial Data
*variables used in our visualization are in blue*

This project uses Caltrans PeMS District 11 data from 2020 and OpenStreetMap road segment data. The final deliverable folder only keeps the processing scripts, the generated HTML maps, and this Rmd file:

```text
PeMS_2020_OSM_deliverable/
├── code/
├── map/
└── PeMS_2020_OSM_processing_report.Rmd
```

The raw PeMS files and intermediate CSV outputs are not copied into this folder because they are large. The code was run in the original project folder, where the raw data, OSM input, and intermediate outputs were available.

```{r}
list.files(".", recursive = TRUE)
```

### 1.1 *Station Metadata*: Provides station locations and station attributes.

Station Metadata is required for map visualization because it connects each PeMS station ID to latitude/longitude coordinates and road attributes.

* <span style="color: blue;">**station**</span>: Unique PeMS station identifier. This is the key used to join metadata with Station Hour, Station Day, and Station 5-Minute tables.

* <span style="color: blue;">**latitude**</span>: Latitude of the station.

* <span style="color: blue;">**longitude**</span>: Longitude of the station.

* <span style="color: blue;">**freeway**</span>: Freeway or route number, such as 5, 15, or 805.

* <span style="color: blue;">**direction**</span>: Travel direction, such as N, S, E, or W.

* <span style="color: blue;">**type**</span>: Station type, such as ML, HV, FR, FF, CD, CH, or OR.

* **lanes**: Number of lanes represented by the station.

* **length**: Segment length represented by the station.

Four 2020 metadata snapshots were used. For each station, the latest available 2020 metadata record was selected for map display.

```{r}
metadata_files <- Sys.glob(file.path("..", "data", "raw", "d11_text_meta_2020_*.txt"))

if (length(metadata_files) > 0) {
  metadata_preview <- read.csv(
    metadata_files[1],
    nrows = 10,
    header = FALSE,
    check.names = FALSE
  )
  metadata_preview
} else {
  message("Raw metadata files are not included in this deliverable folder.")
}
```

### 1.2 *Station Hour*: Provides hourly station-level traffic measurements.

Station Hour contains hourly totals for each active station. This dataset was used to create the monthly and annual station-level map.

* <span style="color: blue;">**timestamp**</span>: Beginning time of the hourly summary interval.

* <span style="color: blue;">**station**</span>: PeMS station identifier.

* <span style="color: blue;">**samples**</span>: Number of valid samples received during the hour.

* <span style="color: blue;">**total_flow**</span>: Total vehicle flow for the hour.

* <span style="color: blue;">**average_speed**</span>: Average speed for the hour.

* **percentage_observed**: Completeness percentage for observed 5-minute lane points.

* **lane_type**: Station or lane category used for filtering.

In preprocessing, hourly values were aggregated by station and month. The weighted metrics use `samples` as weights, so hours with more valid observations have more influence.

```{r}
hour_files <- Sys.glob(file.path("..", "data", "raw", "d11_text_station_hour_2020_*.txt"))

if (length(hour_files) > 0) {
  station_hour <- read.csv(
    hour_files[1],
    nrows = 10,
    header = FALSE,
    check.names = FALSE
  )
  station_hour
} else {
  message("Raw Station Hour files are not included in this deliverable folder.")
}
```

### 1.3 *Station Day*: Provides daily station-level traffic totals.

Station Day contains daily totals for each active station. This dataset was used to create the date-level map.

* <span style="color: blue;">**date**</span>: Date of the daily summary.

* <span style="color: blue;">**station**</span>: PeMS station identifier.

* <span style="color: blue;">**route**</span>: Route or freeway number.

* <span style="color: blue;">**direction_of_travel**</span>: Travel direction.

* <span style="color: blue;">**lane_type**</span>: Station type.

* <span style="color: blue;">**samples**</span>: Number of samples.

* <span style="color: blue;">**percentage_observed**</span>: Data completeness percentage.

* <span style="color: blue;">**total_flow**</span>: Daily total vehicle flow.

```{r}
day_files <- Sys.glob(file.path("..", "data", "raw", "d11_text_station_day_2020_*.txt"))

if (length(day_files) > 0) {
  station_day <- read.csv(
    day_files[1],
    nrows = 10,
    header = FALSE,
    check.names = FALSE
  )
  station_day
} else {
  message("Raw Station Day files are not included in this deliverable folder.")
}
```

### 1.4 *Station 5-Minute*: Provides fine-grained station-level traffic measurements.

Station 5-Minute is the finest time resolution used in this project. Seven days of data were processed, from 2020-10-05 to 2020-10-11. The data was aggregated by station and time of day to create a typical daily 5-minute profile.

* <span style="color: blue;">**timestamp**</span>: Beginning time of the 5-minute interval.

* <span style="color: blue;">**station**</span>: PeMS station identifier.

* <span style="color: blue;">**samples**</span>: Number of samples.

* <span style="color: blue;">**total_flow**</span>: Total flow during the 5-minute interval.

* <span style="color: blue;">**average_speed**</span>: Average speed during the 5-minute interval.

* **occupancy**: Average occupancy during the interval.

* **lane measurements**: Additional lane-level flow, occupancy, and speed columns.

```{r}
five_min_files <- Sys.glob(file.path("..", "data", "raw", "d11_text_station_5min_2020_10_*.txt"))

if (length(five_min_files) > 0) {
  station_5min <- read.csv(
    five_min_files[1],
    nrows = 10,
    header = FALSE,
    check.names = FALSE
  )
  station_5min
} else {
  message("Raw Station 5-Minute files are not included in this deliverable folder.")
}
```

### 1.5 *OpenStreetMap highway data*: Provides road segments for map visualization.

The OSM highway data was used to draw road segments near PeMS stations. Instead of only showing isolated station circles, the visualization also colors nearby OSM road segments based on station traffic values.

* <span style="color: blue;">**way geometry**</span>: Polyline geometry of each OSM highway segment.

* <span style="color: blue;">**highway tag**</span>: OSM road class, such as motorway, trunk, primary, or secondary.

* **name/ref**: Road name or route reference when available.

```{r}
osm_path <- file.path("..", "data", "osm", "d11_highways_overpass.json")

if (file.exists(osm_path)) {
  file.info(osm_path)[, c("size", "mtime")]
} else {
  message("OSM JSON input is not included in this deliverable folder.")
}
```

### 1.6 *AADT data*: Checked but not used in the final maps.

AADT was considered for an additional annual traffic map, but the available 2020 files were incomplete. Only January, April, and June were valid at the time of processing. Several other downloaded AADT entries were only 22 bytes, which indicates no usable data.

Because the 2020 AADT set was not complete, AADT was not included in the final visualizations.

## 2.Main Code

This code is a data preprocessing and geospatial visualization pipeline for PeMS District 11 traffic data. It checks raw file integrity, processes Station Hour, Station Day, Station 5-Minute, and Station Metadata tables, joins traffic measurements to station locations, matches station points to nearby OSM highway segments, and exports standalone HTML maps for visual exploration.

The Python scripts below are included as source code documentation. They are not automatically executed when knitting this Rmd. To rerun the full pipeline, run the scripts from the original project folder where the raw data and OSM input files are available.

```{python eval=FALSE}
# Recommended execution order from the original project folder:

python3 scripts/check_raw_files.py data/raw

python3 scripts/process_station_hour_2020.py
python3 scripts/process_station_day_2020.py
python3 scripts/process_station_5min_week.py

python3 scripts/build_osm_station_hour_map.py
python3 scripts/build_osm_station_day_and_5min_maps.py
```

### 2.1 *check_raw_files.py*: Checks whether downloaded raw files are recognizable and usable.

This script scans `data/raw/`, recognizes PeMS file types from filenames, checks for empty files, and reports missing or suspicious downloads. It was used to verify that Station Hour, Station Day, Station 5-Minute, and Metadata files were usable, and that AADT was still incomplete.

### 2.2 *process_station_hour_2020.py*: Processes metadata and Station Hour files.

This script reads the 2020 metadata snapshots, keeps the latest metadata record for each station, reads all 12 Station Hour monthly files, and creates station-month summaries. The main output is used by `station_hour_2020_osm_map.html`.

### 2.3 *process_station_day_2020.py*: Processes Station Day files.

This script reads all 12 Station Day monthly files and produces a daily station-level flow table. The main output is used by `station_day_2020_osm_map.html`.

### 2.4 *process_station_5min_week.py*: Processes one week of Station 5-Minute files.

This script reads Station 5-Minute data from 2020-10-05 to 2020-10-11, aggregates it by station and time of day, and creates a typical daily 5-minute profile. The main output is used by `station_5min_2020_10_week_osm_map.html`.

### 2.5 *build_osm_station_hour_map.py*: Builds the Station Hour OSM map.

This script joins Station Hour summaries with metadata, matches stations to nearby OSM highway segments, embeds the data into a Leaflet HTML page, and writes the Station Hour map.

### 2.6 *build_osm_station_day_and_5min_maps.py*: Builds the Station Day and Station 5-Minute OSM maps.

This script reuses the OSM road matching logic and creates two additional HTML maps: one for daily station flow and one for 5-minute time-of-day flow.

The copied scripts can be displayed from the `code/` folder:

```{r show-python-scripts, echo=FALSE, results='asis'}
show_script <- function(path) {
  cat("\n### ", basename(path), "\n\n", sep = "")
  if (file.exists(path)) {
    cat("```python\n")
    cat(readLines(path, warn = FALSE), sep = "\n")
    cat("\n```\n")
  } else {
    cat("`", path, "` is missing.\n\n", sep = "")
  }
}

script_files <- c(
  "code/check_raw_files.py",
  "code/process_station_hour_2020.py",
  "code/process_station_day_2020.py",
  "code/process_station_5min_week.py",
  "code/build_osm_station_hour_map.py",
  "code/build_osm_station_day_and_5min_maps.py"
)

invisible(lapply(script_files, show_script))
```

## 3.Output Maps

The final output maps are stored in the `map/` folder. These HTML files are standalone visualization files with embedded station and road-segment data. They still require an internet connection to load the OpenStreetMap basemap tiles.

### 3.1 *station_hour_2020_osm_map.html*

This map shows 2020 Station Hour summaries. It supports monthly selection, annual weighted average selection, station type filters, freeway filters, station search, station circles, and colored OSM road segments.

### 3.2 *station_day_2020_osm_map.html*

This map shows 2020 Station Day daily flow. It supports date selection and road segment coloring based on daily traffic volume.

### 3.3 *station_5min_2020_10_week_osm_map.html*

This map shows a typical daily 5-minute traffic profile based on data from 2020-10-05 to 2020-10-11. It includes a time slider for exploring traffic changes during the day.

```{r}
map_files <- list.files("map", pattern = "\\.html$", full.names = TRUE)
map_files
```

## 4.Current Limitations

* AADT is not included in the final maps because the available 2020 AADT files were incomplete.

* Station Hour and Station Day each contain 14 station IDs that were not matched to the available 2020 metadata snapshots. These stations appear mostly in early 2020 and may require an earlier metadata snapshot.

* Station 5-Minute uses one week of data, so it is suitable for showing a typical daily pattern but not a full-year 5-minute result.

* The HTML files depend on online OpenStreetMap basemap tiles. The station and road-segment data are embedded, but the basemap requires network access.
