---
title: "data_process"
output: html_document
---

## 1.Initial Data
*variables used in our application are in blue*

### 1.1 *ca_meta.csv*: Represents PeMS stations in California.
* <span style="color: blue;">**ID**</span>: Unique PeMS station ID.

* <span style="color: blue;">**Lat**</span>: Latitude of the station.

* <span style="color: blue;">**Lng**</span>: Longitude of the station.

* **District**: Caltrans district number.

* <span style="color: blue;">**County**</span>: County where the station is located.

* <span style="color: blue;">**Fwy**</span>: Freeway or route number.

* **Lanes**: Number of lanes for the station.

* **Type**: Station type. In LargeST, the selected sensors are mainline sensors.

* <span style="color: blue;">**Direction**</span>: Travel direction, such as N, S, E, or W.

* <span style="color: blue;">**ID2**</span>: Column index used to match the station with the h5 flow matrix.

```{r}
ca_meta <- read.csv("data/ca_meta.csv", nrows = 10, check.names = FALSE)
ca_meta
```

### 1.2 *ca_his_raw_2019.h5*: Represents 5-minute station-level traffic flow.
The h5 file stores traffic flow in matrix form. The row index is time, and the column index is station.

* <span style="color: blue;">**t/axis0**</span>: Station ID order.

* <span style="color: blue;">**t/axis1**</span>: Timestamp order.

* <span style="color: blue;">**t/block0_values**</span>: Flow values. Each row is one time step and each column is one station.

```{r}
file.info("data/ca_his_raw_2019.h5")[, c("size", "mtime")]
```

### 1.3 *largest.zip*: Original LargeST archive.
The Kaggle archive contains the California metadata file, yearly 5-minute flow h5 files from 2017 to 2021, and `ca_rn_adj.npy`.

```{r}
file.info("data/largest.zip")[, c("size", "mtime")]
```

### 1.4 Region selection
The map keeps two California regions from the metadata.

* <span style="color: blue;">**Los Angeles Area**</span>: Los Angeles, Orange, Riverside, San Bernardino, Ventura.

* <span style="color: blue;">**Bay Area**</span>: Alameda, Contra Costa, Marin, Napa, San Francisco, San Mateo, Santa Clara, Solano, Sonoma.

```{r}
meta_all <- read.csv("data/ca_meta.csv", check.names = FALSE)

la_counties <- c(
  "Los Angeles", "Orange", "Riverside", "San Bernardino", "Ventura"
)

bay_counties <- c(
  "Alameda", "Contra Costa", "Marin", "Napa", "San Francisco",
  "San Mateo", "Santa Clara", "Solano", "Sonoma"
)

data.frame(
  region = c("Los Angeles Area", "Bay Area"),
  stations = c(
    sum(meta_all$County %in% la_counties),
    sum(meta_all$County %in% bay_counties)
  )
)
```

## 2.Main Code
The Python code reads LargeST metadata and h5 flow records, selects the counties used in the map, connects nearby stations along the same freeway and direction, and writes a Leaflet html file.

The line color is based on 5-minute flow. The road line is built from station coordinates in `ca_meta.csv`.

```{r show-python-code, echo=FALSE, results='asis'}
script_path <- "code/build_largest_flow_map.py"

cat("```python\n")
cat(readLines(script_path, warn = FALSE), sep = "\n")
cat("\n```\n")
```

## 3.Output Map
### 3.1 *largest_la_bay_area_flow_2019_07_31.html*
* <span style="color: blue;">**Region**</span>: Select Los Angeles Area or Bay Area.

* <span style="color: blue;">**Time**</span>: 5-minute time slider.

* <span style="color: blue;">**road segments**</span>: Station-to-station links colored by flow.

* **station points**: Optional station point layer.

* **road casing**: Optional line casing layer.

```{r}
list.files("map", pattern = "\\.html$", full.names = TRUE)
```

## 4.Notes
* The color scale is flow, not speed.

* The road lines are built from station coordinates in `ca_meta.csv`.

* `ca_rn_adj.npy` is part of the LargeST release, but it is not used for this html map.
