---
title: "city_traffic_data_process"
output: html_document
---

## 1. Initial Data

This document summarizes the data and code used for the current City Traffic Benchmarks visualization work. The final interactive map is built from the Kaggle dataset `mightyneghbor/city-traffic-benchmarks`, version 4, with a focus on `city-traffic-M`.

The raw dataset is much larger than the subset used here. The full dataset contains two city scales (`city-traffic-M` and `city-traffic-L`) and dynamic traffic speed/volume files. For the current visualization, we only downloaded the small static/topology files and the `city-traffic-M` volume file locally. The large `city-traffic-M` speed file is not fully downloaded; the script reads only selected byte ranges for the sampled road segments.

*variables used in the current visualization are in blue*

### 1.1 `city-traffic-M-raw-static-features.parquet`

This file stores static attributes for each directed road segment in `city-traffic-M`.

Local path:

`data/city-traffic-benchmarks/city-traffic-M-raw-static-features.parquet`

Observed shape: 53,530 rows and 26 columns.

* **category**: Numeric road category code.

* **edge_type**: Numeric edge type code.

* **speed_mode**: Encoded speed mode.

* <span style="color: blue;">**speed_limit**</span>: Encoded speed limit. In the visualization it is converted to labels such as `50 km/h`; `0` is treated as unknown.

* <span style="color: blue;">**region_id**</span>: Region identifier used in hover tooltips.

* **can_bind_to_reverse_edge**: Whether the segment can be matched with a reverse edge.

* **dismount_bike**, **has_masstransit_lane**, **ends_with_crosswalk**, **ends_with_toll_post**: Static road flags.

* **is_in_poor_condition**, **is_paved**, **is_restricted_for_trucks**, **is_toll**: Static road condition/access flags.

* **access_0** to **access_5**: Encoded access flags.

* <span style="color: blue;">**length**</span>: Road segment length in meters; used in hover tooltips.

* **num_segments**: Number of geometric subsegments.

* <span style="color: blue;">**x_coordinate_start, y_coordinate_start**</span>: Segment start longitude/latitude.

* <span style="color: blue;">**x_coordinate_end, y_coordinate_end**</span>: Segment end longitude/latitude.

```{r eval=FALSE}
library(arrow)

static_m <- read_parquet("data/city-traffic-benchmarks/city-traffic-M-raw-static-features.parquet")
head(static_m, 10)
names(static_m)
```

### 1.2 `city-traffic-M-raw-edges.parquet`

This file stores the directed road graph topology for `city-traffic-M`.

Local path:

`data/city-traffic-benchmarks/city-traffic-M-raw-edges.parquet`

Observed shape: 121,236 rows and 2 columns.

* **source**: Source road-segment node id in the directed graph.

* **target**: Target road-segment node id in the directed graph.

This file is useful for graph-based modeling or adjacency analysis. The current Leaflet/OSM visualization does not require it because the static features file already contains each road segment's start/end coordinates.

```{r eval=FALSE}
library(arrow)

edges_m <- read_parquet("data/city-traffic-benchmarks/city-traffic-M-raw-edges.parquet")
head(edges_m, 10)
```

### 1.3 `city-traffic-M-raw-volume.parquet`

This file stores dynamic traffic volume values for `city-traffic-M`.

Local path:

`data/city-traffic-benchmarks/city-traffic-M-raw-volume.parquet`

Observed shape: 35,449 rows and 53,531 columns. The native temporal resolution is 5 minutes. The table contains one `timestamp` field and one dynamic column per road segment, named as `node_0`, `node_1`, ..., `node_53529`.

* <span style="color: blue;">**timestamp**</span>: Time index. The local file covers observations from 2024-07-01 to 2024-11-01 02:00.

* <span style="color: blue;">**node_* columns**</span>: Traffic volume for each road segment at each timestamp. For visualization, only 720 sampled road-segment columns are read.

The current visualization aggregates the native 5-minute values into 15-minute mean frames. The sample day is selected automatically as the busiest complete day among the sampled road segments; the current output uses 2024-10-18.

```{r eval=FALSE}
library(arrow)

volume_schema <- open_dataset("data/city-traffic-benchmarks/city-traffic-M-raw-volume.parquet")
volume_schema

# Example: read timestamp and a small number of columns only.
volume_preview <- read_parquet(
  "data/city-traffic-benchmarks/city-traffic-M-raw-volume.parquet",
  col_select = c(timestamp, node_0, node_1, node_2)
)
head(volume_preview, 10)
```

### 1.4 `city-traffic-M-raw-speed.parquet`

This file stores dynamic speed values for `city-traffic-M`.

Local status:

* The full speed file is not stored locally because it is approximately 11 GB.
* Only the Parquet footer is cached at `data/city-traffic-benchmarks/_cache/city-traffic-M-raw-speed.footer.bin`.
* The OSM congestion script obtains a temporary signed Kaggle URL, fetches only the selected column byte ranges, writes a sparse temporary Parquet file, and reads the sampled road segments from that file.

* <span style="color: blue;">**timestamp**</span>: Time index matching the dynamic volume table.

* <span style="color: blue;">**node_* columns**</span>: Traffic speed for each road segment at each timestamp. The current script reads the same 720 sampled `node_*` columns selected from the volume file.

The speed data is used to estimate each segment's empirical free-flow speed as the 90th percentile of observed nonzero speed. The current congestion score then compares each frame's speed to this segment-level baseline.

### 1.5 `city-traffic-L` files

The following larger-city static/topology files are downloaded locally for inspection but are not used in the current visualization:

* `data/city-traffic-benchmarks/city-traffic-L-raw-static-features.parquet`: 94,009 rows and 26 columns.
* `data/city-traffic-benchmarks/city-traffic-L-raw-edges.parquet`: 164,424 rows and 2 columns.

The current dynamic HTML focuses on `city-traffic-M` because its full volume file is locally available and the resulting browser payload is manageable.

## 2. Code Inventory

### 2.1 `scripts/build_city_traffic_dynamic_sample.py`

Path:

`scripts/build_city_traffic_dynamic_sample.py`

Purpose:

This is the first lightweight dynamic visualization script. It reads `city-traffic-M-raw-static-features.parquet` and `city-traffic-M-raw-volume.parquet`, selects 720 road segments with nonzero/high traffic volume using grid-based spatial thinning, aggregates one sample day to 15-minute frames, and writes a custom canvas HTML visualization without an OSM basemap.

Main outputs:

* `visualizations/city_traffic_M_volume_dynamic_sample.html`
* `visualizations/city_traffic_M_volume_sample.json`
* `visualizations/city_traffic_M_volume_sample.js`
* `visualizations/city_traffic_M_volume_dynamic_sample.png`

Main functions:

* `load_static_features()`: reads static road features and computes midpoint coordinates.
* `load_volume_column_stats()`: uses Parquet column statistics to identify road segments with nonzero volume.
* `select_dynamic_segments()`: chooses 720 high-activity but spatially distributed segments.
* `read_volume_timeseries()`: reads only selected volume columns and `timestamp`.
* `choose_sample_day()`: chooses the busiest complete day in the sampled data.
* `make_frames()`: aggregates native 5-minute records into 15-minute mean frames.
* `build_payload()`: creates browser-ready metadata, segment geometry, and frame values.
* `write_payload()` and `write_html()`: write JSON, JS, and HTML artifacts.

Run manually:

```{bash eval=FALSE}
PYTHONPATH=/tmp/codex_pyarrow python3 scripts/build_city_traffic_dynamic_sample.py
```

### 2.2 `scripts/build_city_traffic_osm_congestion_sample.py`

Path:

`scripts/build_city_traffic_osm_congestion_sample.py`

Purpose:

This is the current main script. It creates the Chinese OSM/Leaflet traffic map with two display modes: congestion and volume. It uses local static features and volume data, and range-fetches only the needed speed columns from the remote Kaggle speed Parquet file.

Main outputs:

* `visualizations/city_traffic_M_osm_congestion_sample.html`
* `visualizations/city_traffic_M_osm_congestion_sample.json`
* `visualizations/city_traffic_M_osm_congestion_sample.js`
* `visualizations/city_traffic_M_osm_congestion_sample.png`

Main functions:

* `load_static_features()`: reads static road features and keeps road geometry.
* `load_volume_column_stats()`: reads volume Parquet metadata/statistics without scanning the whole table.
* `select_dynamic_segments()`: selects 720 sampled road segments by high volume and spatial thinning.
* `read_volume_timeseries()`: reads selected volume columns.
* `choose_sample_day()` and `frame_timeseries()`: choose 2024-10-18 and aggregate to 15-minute frames.
* `get_signed_speed_url()`: requests a temporary Kaggle download URL for the large speed file.
* `download_speed_footer()`: caches only the Parquet footer locally.
* `needed_column_ranges()`, `merge_ranges()`, and `write_ranges_to_sparse_file()`: identify and download only the byte ranges needed for selected speed columns.
* `read_speed_subset()`: reads the sparse temporary speed Parquet file.
* `build_payload()`: computes free-flow speed, congestion score, map bounds, segment records, and per-frame values.
* `write_outputs()`: writes JSON, JS, and HTML artifacts.

Run manually:

```{bash eval=FALSE}
PYTHONPATH=/tmp/codex_pyarrow python3 scripts/build_city_traffic_osm_congestion_sample.py
```

## 3. Processing Pipeline

### 3.1 Segment selection

The dynamic map does not render all 53,530 road segments. Instead, it selects 720 active segments for browser performance:

1. Read all static segment geometries from `city-traffic-M-raw-static-features.parquet`.
2. Read Parquet column statistics from `city-traffic-M-raw-volume.parquet`.
3. Keep only `node_*` columns whose maximum volume is greater than zero.
4. Sort candidate segments by maximum observed volume.
5. Apply grid-based spatial thinning so the sample is not only concentrated in the city center.
6. Fill any remaining sample slots with the next highest-volume segments.

This means the current visualization is a high-activity sample, not a full-city rendering.

### 3.2 Temporal aggregation

The original dynamic data uses 5-minute intervals. The browser visualization displays 15-minute frames:

```{python eval=FALSE}
frames = day.resample("15min").mean().interpolate(limit_direction="both")
```

Current sample metadata:

* Sample day: 2024-10-18
* Frame count: 96
* Native time step: 5 minutes
* Display frame interval: 15 minutes
* Current OSM peak congestion frame: 2024-10-18 13:30

### 3.3 Congestion metric

The default visualization mode is congestion rather than raw traffic volume.

For each selected segment, the script estimates:

```text
free_flow_speed = p90(nonzero observed speed for that segment)
```

For each segment and frame:

```text
slowdown = max(0, 1 - current_speed / free_flow_speed)
volume_weight = clipped log1p(current_volume) / log1p(global_volume_p95)
congestion = slowdown * volume_weight
```

This metric highlights roads that are both slow and active. A road that is slow but nearly empty is de-emphasized.

### 3.4 OSM usage

OpenStreetMap is used only as the visual basemap:

* map tiles;
* road/place labels;
* geographic context and orientation.

OSM is not used to calculate congestion or flow. The congestion calculation uses only the dataset's static geometry, dynamic volume, and dynamic speed values.

The HTML uses Leaflet 1.9.4 and the OSM tile endpoint:

```{javascript eval=FALSE}
L.tileLayer("https://tile.openstreetmap.org/{z}/{x}/{y}.png", {
  maxZoom: 19,
  attribution: '&copy; <a href="https://www.openstreetmap.org/copyright">OpenStreetMap</a> contributors'
}).addTo(map);
```

## 4. Visualization Outputs

### 4.1 Current main output

Open:

`visualizations/city_traffic_M_osm_congestion_sample.html`

The page is a Chinese interactive map. It has:

* OSM basemap;
* `拥堵` and `流量` display modes;
* play/pause animation;
* frame slider;
* top KPI cards;
* current time window details;
* hover tooltip for each displayed road segment;
* trend chart for the selected metric.

### 4.2 Color encoding

In `拥堵` mode:

* Green means smoother traffic.
* Yellow means slower traffic.
* Red means more severe congestion.
* Wider line means higher metric value.

In `流量` mode:

* Green means low traffic volume.
* Yellow means medium traffic volume.
* Red means high traffic volume.
* Wider line means higher volume.

The traffic lines also have a dark halo stroke and the OSM tile layer is slightly desaturated so the traffic colors are more visible against the basemap.

### 4.3 Browser-ready data files

The OSM HTML loads:

* `visualizations/city_traffic_M_osm_congestion_sample.js`

This JS file defines:

```{javascript eval=FALSE}
window.CITY_TRAFFIC_OSM_SAMPLE = { ... }
```

The same payload is also stored in:

* `visualizations/city_traffic_M_osm_congestion_sample.json`

Important payload sections:

* `metadata`: source files, sample day, frame count, segment count, metric definitions.
* `bounds`: map bounds for fitting the initial Leaflet view.
* `segments`: static segment geometry and tooltip attributes.
* `frames`: per-frame congestion, volume, speed, and summary metrics.

## 5. Main Code

The Python chunks below are included as source-code documentation (`eval=FALSE`). Knitting this Rmd will not automatically run the preprocessing pipeline.

### 5.1 Current OSM congestion visualization script

```{python eval=FALSE}
# File:
# scripts/build_city_traffic_osm_congestion_sample.py

# Key command:
# PYTHONPATH=/tmp/codex_pyarrow python3 scripts/build_city_traffic_osm_congestion_sample.py

# High-level flow:
# 1. Read static road geometry from city-traffic-M-raw-static-features.parquet.
# 2. Read volume Parquet column statistics and select 720 active road segments.
# 3. Read selected volume columns and choose the busiest complete sample day.
# 4. Fetch only selected speed columns from the remote city-traffic-M speed file.
# 5. Aggregate both volume and speed to 15-minute frames.
# 6. Compute segment p90 speed as the free-flow baseline.
# 7. Compute congestion = relative slowdown * clipped log-volume weight.
# 8. Write the Leaflet/OSM HTML, JSON, and JS files.
```

To inspect the full script inside R:

```{r eval=FALSE}
cat(readLines("scripts/build_city_traffic_osm_congestion_sample.py"), sep = "\n")
```

### 5.2 Earlier volume-only visualization script

```{python eval=FALSE}
# File:
# scripts/build_city_traffic_dynamic_sample.py

# Key command:
# PYTHONPATH=/tmp/codex_pyarrow python3 scripts/build_city_traffic_dynamic_sample.py

# High-level flow:
# 1. Read static road geometry.
# 2. Read volume column statistics.
# 3. Select 720 dynamic road segments and 6,400 background road segments.
# 4. Read selected volume columns.
# 5. Choose the busiest complete sample day.
# 6. Aggregate native 5-minute volume to 15-minute frames.
# 7. Write a non-OSM custom canvas HTML visualization.
```

To inspect the full script inside R:

```{r eval=FALSE}
cat(readLines("scripts/build_city_traffic_dynamic_sample.py"), sep = "\n")
```

## 6. Reproducibility Notes

The current project directory is not a Git repository, so code history is not available from `git status` or `git diff` here.

The current OSM visualization was browser-tested with Chrome/Playwright after generation. The verified state included:

* 96 frames;
* 720 road segments;
* loaded OSM tiles;
* working default `拥堵` mode;
* working switch to `流量` mode;
* no browser page errors.

If the OSM page is opened offline, the local overlay data will still exist, but the OSM basemap tiles may not load.
