---
title: "data_process"
output: html_document
---

## 1.Initial Data
### 1.1 *input_node.csv*: Represents the intersections or endpoints on the map.
* **name**: Intersection or node name.

* <span style="color: blue;">**node_id**: Unique identifier for the node.

* **control_type**: Numeric code representing the traffic control method.

* **control_type_name**: Descriptive name of the traffic control method (e.g., no_control, signalized, stop_sign).

* **cycle_length_in_second**: Total traffic signal cycle duration, in seconds.

* <span style="color: blue;">**x**: Spatial X-coordinate (typically longitude or projected X).

* <span style="color: blue;">**y**: Spatial Y-coordinate (typically latitude or projected Y).

* **geometry**: GIS spatial data format (e.g., Point coordinates) for mapping and visualization.
```{r}
input_node <- read.csv("input_node.csv", nrows = 10, check.names = FALSE)
input_node
```

### 1.2 *input_link.csv*: Represents the specific road segments connecting the nodes.
* **name**: The street or road name.

* **link_id**: Unique numerical identifier for the road segment.

* **link_key**: Directional unique identifier.

* <span style="color: blue;">**from_node_id & to_node_id**: The origin and destination node IDs defining the topological connection.

* <span style="color: blue;">**length**: The physical length of the segment.

* <span style="color: blue;">**direction**: Traffic flow directionality.

* **number_of_lanes**: Number of Lanes.

* **speed_limit**: Free-flow speed or regulatory speed limit.

* **grade**: The longitudinal slope of the road.

* **geometry & original_geometry**: The spatial linestring data (coordinates) used for GIS visualization.

* **link_type_name & link_type**: Classification of the road (e.g., arterial, highway, connector).

* **lane_capacity_in_vhc_per_hour**: Maximum vehicle throughput per lane per hour.

* **jam_density**: The extreme traffic density when traffic flow stops completely.

* **wave_speed**: The speed at which traffic congestion waves propagate backward.

* **peed_sensor_id & count_sensor_id**: Identifiers for physical sensors mapped to this link.

* **demand_type_code & mode_code**: Allowed transportation modes.

* **network_design_flag**: Indicates if the link is modified for scenario testing.

* **map_matching_orientation_code & map_matching_loop_code**: Used by algorithms to snap GPS points to this specific link.
```{r}
input_link <- read.csv("input_link.csv", nrows = 10, check.names = FALSE)
input_link
```

### 1.3 *output_agent.csv*: Represents the complete trip records of each individual vehicle generated by the simulation system.
* **agent_id**: The unique numerical identifier for each individual vehicle.

* **vehicle_type**: The classification of the vehicle.

* **o_zone_id & d_zone_id**: The traffic analysis zones where the trip starts and ends.

* **from_origin_node_id & to_destination_node_id**: The exact physical intersections (nodes) where the vehicle enters and exits the network.

* **departure_time_in_min & departure_time_in_hhmm**: The time the trip begins, recorded in total minutes and HH:MM format.

* **arrival_time_in_min & arrival_time_in_hhmm**: The time the trip ends.

* **travel_time_in_min**: Total duration of the trip.

* **travel_distance_in_km**: Total physical distance covered.

* **delay_in_min**: The extra time spent in traffic compared to free-flow conditions.

* **information_type**: Indicates whether the agent has access to real-time routing information.

* **value_of_time**: Economic measure of how much the driver values saving time.

* **PCE**: A metric assessing the vehicle's impact on traffic flow relative to a standard passenger car.

* **toll_cost**: Total monetary charges incurred during the trip.

* <span style="color: blue;">**path_node_sequence**: Ordered list of all node IDs visited.

* **path_link_sequence**: Ordered list of all link IDs traveled.

* <span style="color: blue;">**path_time_sequence**: The travel time spent on each individual link.

* **path_distance_sequence**: The distance of each individual link traveled.

* **node_arrival_time_sequence**: Timestamps for when the vehicle arrives at each node.

* **node_departure_time_sequence**: Timestamps for when the vehicle departs from each node.
```{r}
output_agent <- read.csv("output_agent.csv", nrows = 10, check.names = FALSE)
output_agent
```

## 2.Main Code
This code is a comprehensive data preprocessing and spatiotemporal feature extraction pipeline designed for traffic simulation outputs. It ingests raw road network data (nodes and links) alongside microscopic vehicle trajectories to construct structured, spatiotemporal datasets. Specifically, the code cleans the network topology and coordinates, aggregates individual vehicle trips into macroscopic dynamic edge flows ($x_{ijt}$) and node flows ($x_{it}$) over discrete time bins (e.g., 5-minute intervals), and computationally extracts spatial adjacency relationships (such as upstream/downstream and shortest-path neighbors) for both nodes and edges. Ultimately, it exports these multifaceted traffic states and topological features into standardized tabular formats (including wide tables), establishing a highly organized data foundation for downstream traffic visualization or graph-based machine learning tasks (like GNN models).

```{python eval=FALSE}
import math
import heapq
from pathlib import Path
from collections import defaultdict, Counter

import numpy as np
import pandas as pd

try:
    from tqdm import tqdm
except Exception:
    def tqdm(x, **kwargs):
        return x


# ============================================================
# Config
# ============================================================

TIME_BIN_MIN = 5

# "entry" means a vehicle is counted only when it enters an edge.
# "occupancy" means a vehicle is counted in every time bin it stays on the edge.
EDGE_FLOW_MODE = "occupancy"

FULL_DAY_MINUTES = 1440
FORCE_FULL_DAY = True

# If FORCE_FULL_DAY = True and this is True, only [0, 1440) is kept.
# A trip segment crossing 1440 will be clipped to the last valid bin.
CLIP_FLOW_TO_TIME_PANEL = True

KEEP_ONLY_COMPLETED_AGENTS = True
USE_PCE_AS_WEIGHT = False

COMPLETE_EDGE_TIME_PANEL = True
WRITE_WIDE_TABLES = True

USE_MOE_FEATURES = False

K_NEAREST_NODES = 10
NODE_DISTANCE_RADIUS = None

MAKE_NETWORK_PREVIEW = True

OUTPUT_DIR = "processed_real_network"

EPS = 1e-9


# ============================================================
# IO helpers
# ============================================================

def find_file(base_dir, candidates):
    base = Path(base_dir)
    lower_map = {p.name.lower(): p for p in base.iterdir() if p.is_file()}

    for name in candidates:
        p = base / name
        if p.exists():
            return p

    for name in candidates:
        p = lower_map.get(name.lower())
        if p is not None:
            return p

    return None


def read_csv_auto(path):
    encodings = ["utf-8-sig", "utf-8", "gbk", "latin1"]

    last_error = None
    for enc in encodings:
        try:
            df = pd.read_csv(
                path,
                encoding=enc,
                skipinitialspace=True,
                engine="python",
                on_bad_lines="warn"
            )
            df.columns = [str(c).strip() for c in df.columns]
            df = df.loc[:, ~pd.Index(df.columns).str.startswith("Unnamed")]
            df = df.loc[:, [str(c).strip() != "" for c in df.columns]]
            return df
        except Exception as e:
            last_error = e

    raise RuntimeError(f"Could not read {path}. Last error: {last_error}")


def to_num(s):
    return pd.to_numeric(s, errors="coerce")


def clean_colnames(df):
    df = df.copy()
    df.columns = [str(c).strip() for c in df.columns]
    return df


def parse_semicolon_ints(value):
    if pd.isna(value):
        return []

    parts = str(value).replace('"', "").strip().split(";")
    out = []

    for p in parts:
        p = p.strip()
        if p == "":
            continue
        try:
            out.append(int(float(p)))
        except Exception:
            pass

    return out


def parse_semicolon_floats(value):
    if pd.isna(value):
        return []

    parts = str(value).replace('"', "").strip().split(";")
    out = []

    for p in parts:
        p = p.strip()
        if p == "":
            continue
        try:
            out.append(float(p))
        except Exception:
            pass

    return out


def safe_int(x):
    try:
        if pd.isna(x):
            return None
        return int(float(x))
    except Exception:
        return None


def get_attr(row, col):
    return getattr(row, col) if hasattr(row, col) else np.nan


# ============================================================
# Nodes
# ============================================================

def build_nodes(base_dir, out_dir):
    node_path = find_file(base_dir, ["input_node.csv"])
    node_wgs_path = find_file(base_dir, ["input_node_WGS84.csv", "input_node_wgs84.csv"])

    if node_path is None:
        raise FileNotFoundError("Missing input_node.csv")

    nodes = read_csv_auto(node_path)
    nodes = clean_colnames(nodes)

    required = ["node_id", "x", "y"]
    for col in required:
        if col not in nodes.columns:
            raise ValueError(f"input_node.csv is missing required column: {col}")

    nodes["node_id"] = to_num(nodes["node_id"]).astype("Int64")
    nodes["x"] = to_num(nodes["x"])
    nodes["y"] = to_num(nodes["y"])

    keep_cols = [
        c for c in [
            "name",
            "node_id",
            "control_type",
            "control_type_name",
            "cycle_length_in_second",
            "x",
            "y",
            "geometry"
        ]
        if c in nodes.columns
    ]

    nodes = nodes[keep_cols].dropna(subset=["node_id"])
    nodes["node_id"] = nodes["node_id"].astype(int)
    nodes = nodes.drop_duplicates("node_id")

    if node_wgs_path is not None:
        wgs = read_csv_auto(node_wgs_path)
        wgs = clean_colnames(wgs)

        if "node_id" in wgs.columns:
            wgs["node_id"] = to_num(wgs["node_id"]).astype("Int64")
            extra_cols = [c for c in ["node_id", "x_84", "y_84"] if c in wgs.columns]

            if "x_84" in extra_cols and "y_84" in extra_cols:
                wgs = wgs[extra_cols].dropna(subset=["node_id"])
                wgs["node_id"] = wgs["node_id"].astype(int)
                nodes = nodes.merge(wgs.drop_duplicates("node_id"), on="node_id", how="left")

    nodes.to_csv(out_dir / "nodes_clean.csv", index=False)
    return nodes


# ============================================================
# Links
# ============================================================

def estimate_length_from_coords(from_node, to_node, coord_map):
    if from_node not in coord_map or to_node not in coord_map:
        return np.nan

    x1, y1 = coord_map[from_node]
    x2, y2 = coord_map[to_node]

    dist_meter = math.sqrt((x1 - x2) ** 2 + (y1 - y2) ** 2)
    return dist_meter / 1000.0


def build_links(base_dir, out_dir, nodes):
    link_path = find_file(base_dir, ["input_link.csv"])

    if link_path is None:
        raise FileNotFoundError("Missing input_link.csv")

    raw = read_csv_auto(link_path)
    raw = clean_colnames(raw)

    required = ["from_node_id", "to_node_id"]
    for col in required:
        if col not in raw.columns:
            raise ValueError(f"input_link.csv is missing required column: {col}")

    coord_map = {
        int(r.node_id): (float(r.x), float(r.y))
        for r in nodes[["node_id", "x", "y"]].dropna().itertuples(index=False)
    }

    rows = []

    for r in tqdm(raw.itertuples(index=False), total=len(raw), desc="Cleaning links"):
        from_node = safe_int(get_attr(r, "from_node_id"))
        to_node = safe_int(get_attr(r, "to_node_id"))

        if from_node is None or to_node is None:
            continue

        direction = safe_int(get_attr(r, "direction"))
        if direction is None:
            direction = 1

        if direction == -1:
            directed_pairs = [(to_node, from_node, "reversed")]
        elif direction in [0, 2]:
            directed_pairs = [
                (from_node, to_node, "forward"),
                (to_node, from_node, "backward")
            ]
        else:
            directed_pairs = [(from_node, to_node, "forward")]

        for u, v, direction_flag in directed_pairs:
            length = pd.to_numeric(get_attr(r, "length"), errors="coerce")

            if pd.isna(length) or length <= 0:
                length = estimate_length_from_coords(u, v, coord_map)

            rows.append({
                "from_node_id": u,
                "to_node_id": v,
                "direction_flag": direction_flag,
                "original_link_id": get_attr(r, "link_id"),
                "original_link_key": get_attr(r, "link_key"),
                "name": get_attr(r, "name"),
                "link_type_name": get_attr(r, "link_type_name"),
                "length": length,
                "number_of_lanes": get_attr(r, "number_of_lanes"),
                "speed_limit": get_attr(r, "speed_limit"),
                "lane_capacity_in_vhc_per_hour": get_attr(r, "lane_capacity_in_vhc_per_hour"),
                "link_type": get_attr(r, "link_type"),
                "jam_density": get_attr(r, "jam_density"),
                "wave_speed": get_attr(r, "wave_speed"),
                "geometry": get_attr(r, "geometry"),
                "original_geometry": get_attr(r, "original_geometry")
            })

    directed = pd.DataFrame(rows)

    if len(directed) == 0:
        raise ValueError("No valid links were created from input_link.csv")

    numeric_cols = [
        "length",
        "number_of_lanes",
        "speed_limit",
        "lane_capacity_in_vhc_per_hour",
        "link_type",
        "jam_density",
        "wave_speed"
    ]

    for c in numeric_cols:
        if c in directed.columns:
            directed[c] = to_num(directed[c])

    agg_dict = {
        "length": "min",
        "number_of_lanes": "sum",
        "speed_limit": "mean",
        "lane_capacity_in_vhc_per_hour": "sum",
        "link_type": "first",
        "jam_density": "mean",
        "wave_speed": "mean",
        "name": "first",
        "link_type_name": "first",
        "geometry": "first",
        "original_geometry": "first",
        "direction_flag": lambda x: ";".join(sorted(set(map(str, x)))),
        "original_link_id": lambda x: ";".join(map(str, x)),
        "original_link_key": lambda x: ";".join(map(str, x))
    }

    links = (
        directed
        .groupby(["from_node_id", "to_node_id"], as_index=False)
        .agg(agg_dict)
    )

    links = links.sort_values(["from_node_id", "to_node_id"]).reset_index(drop=True)
    links.insert(0, "edge_index", np.arange(len(links)))
    links["edge_id"] = links["from_node_id"].astype(str) + "->" + links["to_node_id"].astype(str)

    links.to_csv(out_dir / "links_clean.csv", index=False)
    return links


# ============================================================
# x_ijt from output_agent.csv
# ============================================================

def get_time_bins_for_segment(t_enter, t_exit):
    """
    For EDGE_FLOW_MODE = "occupancy":
    Count all bins overlapped by [t_enter, t_exit).

    Example if TIME_BIN_MIN = 1:
        [1.8, 2.2) -> bins 1 and 2
        [1.8, 2.0) -> bin 1 only
        [2.0, 2.2) -> bin 2 only
    """

    if not np.isfinite(t_enter) or not np.isfinite(t_exit):
        return []

    if t_enter < 0 and t_exit < 0:
        return []

    if t_exit < t_enter:
        return []

    panel_start = 0.0
    panel_end = FULL_DAY_MINUTES if FORCE_FULL_DAY and CLIP_FLOW_TO_TIME_PANEL else None

    start = max(t_enter, panel_start)
    end = t_exit

    if panel_end is not None:
        end = min(end, panel_end)

    if end < start:
        return []

    if abs(end - start) <= EPS:
        if panel_end is not None and start >= panel_end:
            return []
        return [int(math.floor(start / TIME_BIN_MIN))]

    start_bin = int(math.floor(start / TIME_BIN_MIN))
    end_bin = int(math.floor((end - EPS) / TIME_BIN_MIN))

    if end_bin < start_bin:
        return []

    return list(range(start_bin, end_bin + 1))


def get_time_bin_for_entry(t_enter):
    if not np.isfinite(t_enter) or t_enter < 0:
        return None

    if FORCE_FULL_DAY and CLIP_FLOW_TO_TIME_PANEL:
        if t_enter >= FULL_DAY_MINUTES:
            return None

    return int(math.floor(t_enter / TIME_BIN_MIN))


def build_edge_flow(base_dir, out_dir, links):
    agent_path = find_file(base_dir, ["output_agent.csv", "Output_agent.csv"])

    if agent_path is None:
        raise FileNotFoundError("Missing output_agent.csv")

    if EDGE_FLOW_MODE not in ["entry", "occupancy"]:
        raise ValueError("EDGE_FLOW_MODE must be either 'entry' or 'occupancy'")

    agents = read_csv_auto(agent_path)
    agents = clean_colnames(agents)

    required = ["path_node_sequence", "path_time_sequence"]
    for col in required:
        if col not in agents.columns:
            raise ValueError(f"output_agent.csv is missing required column: {col}")

    pair_to_edge_id = {
        (int(r.from_node_id), int(r.to_node_id)): r.edge_id
        for r in links[["from_node_id", "to_node_id", "edge_id"]].itertuples(index=False)
    }

    pair_to_edge_index = {
        (int(r.from_node_id), int(r.to_node_id)): int(r.edge_index)
        for r in links[["from_node_id", "to_node_id", "edge_index"]].itertuples(index=False)
    }

    valid_pairs = set(pair_to_edge_id.keys())

    flow_counter = defaultdict(float)
    missing_counter = Counter()

    total_agents = 0
    used_agents = 0
    bad_agents = 0

    total_edge_traversals = 0
    used_edge_traversals = 0
    missing_edge_traversals = 0

    counted_edge_segments = 0
    skipped_time_segments = 0
    bad_time_segments = 0
    occupancy_bin_updates = 0

    max_time_seen = 0.0

    has_complete_flag = "complete_flag" in agents.columns
    has_pce = "PCE" in agents.columns

    for r in tqdm(agents.itertuples(index=False), total=len(agents), desc="Parsing agent paths"):
        total_agents += 1

        if KEEP_ONLY_COMPLETED_AGENTS and has_complete_flag:
            flag = str(get_attr(r, "complete_flag")).strip().lower()
            if flag != "c":
                continue

        nodes_seq = parse_semicolon_ints(get_attr(r, "path_node_sequence"))
        times_seq = parse_semicolon_floats(get_attr(r, "path_time_sequence"))

        m = min(len(nodes_seq), len(times_seq))

        if m < 2:
            bad_agents += 1
            continue

        used_agents += 1

        if len(times_seq) > 0:
            max_time_seen = max(max_time_seen, max(times_seq))

        if USE_PCE_AS_WEIGHT and has_pce:
            try:
                weight = float(get_attr(r, "PCE"))
            except Exception:
                weight = 1.0
        else:
            weight = 1.0

        for k in range(m - 1):
            u = nodes_seq[k]
            v = nodes_seq[k + 1]
            t_enter = times_seq[k]
            t_exit = times_seq[k + 1]

            if not np.isfinite(t_enter) or not np.isfinite(t_exit):
                bad_time_segments += 1
                continue

            if t_exit < t_enter:
                bad_time_segments += 1
                continue

            total_edge_traversals += 1

            if (u, v) not in valid_pairs:
                missing_counter[(u, v)] += 1
                missing_edge_traversals += 1
                continue

            used_edge_traversals += 1

            if EDGE_FLOW_MODE == "entry":
                time_bin = get_time_bin_for_entry(t_enter)

                if time_bin is None:
                    skipped_time_segments += 1
                    continue

                flow_counter[(time_bin, u, v)] += weight
                counted_edge_segments += 1
                occupancy_bin_updates += 1

            else:
                bins = get_time_bins_for_segment(t_enter, t_exit)

                if len(bins) == 0:
                    skipped_time_segments += 1
                    continue

                counted_edge_segments += 1

                for time_bin in bins:
                    flow_counter[(time_bin, u, v)] += weight
                    occupancy_bin_updates += 1

    rows = []

    for (time_bin, u, v), val in tqdm(flow_counter.items(), total=len(flow_counter), desc="Writing nonzero x_ijt"):
        rows.append({
            "time_bin": time_bin,
            "start_min": time_bin * TIME_BIN_MIN,
            "end_min": (time_bin + 1) * TIME_BIN_MIN,
            "edge_index": pair_to_edge_index[(u, v)],
            "edge_id": pair_to_edge_id[(u, v)],
            "from_node_id": u,
            "to_node_id": v,
            "x_ijt": val
        })

    flow_nz = pd.DataFrame(rows)

    if len(flow_nz) == 0:
        flow_nz = pd.DataFrame(
            columns=[
                "time_bin",
                "start_min",
                "end_min",
                "edge_index",
                "edge_id",
                "from_node_id",
                "to_node_id",
                "x_ijt"
            ]
        )

    flow_nz = flow_nz.sort_values(["time_bin", "from_node_id", "to_node_id"]).reset_index(drop=True)
    flow_nz.to_csv(out_dir / "edge_flow_xijt_nonzero.csv", index=False)

    if FORCE_FULL_DAY:
        n_bins = int(math.ceil(FULL_DAY_MINUTES / TIME_BIN_MIN))
    else:
        max_bin = int(math.floor(max_time_seen / TIME_BIN_MIN)) if max_time_seen > 0 else 0
        max_bin_from_flow = int(flow_nz["time_bin"].max()) if len(flow_nz) > 0 else 0
        n_bins = max(max_bin, max_bin_from_flow) + 1

    time_df = pd.DataFrame({"time_bin": np.arange(n_bins, dtype=int)})
    time_df["start_min"] = time_df["time_bin"] * TIME_BIN_MIN
    time_df["end_min"] = (time_df["time_bin"] + 1) * TIME_BIN_MIN

    if COMPLETE_EDGE_TIME_PANEL:
        print("Building complete edge-time panel...")

        time_idx = pd.DataFrame({
            "time_bin": np.repeat(time_df["time_bin"].values, len(links)),
            "start_min": np.repeat(time_df["start_min"].values, len(links)),
            "end_min": np.repeat(time_df["end_min"].values, len(links))
        })

        link_idx = pd.concat(
            [links[["edge_index", "edge_id", "from_node_id", "to_node_id"]]] * len(time_df),
            ignore_index=True
        )

        panel = pd.concat([time_idx, link_idx], axis=1)

        panel = panel.merge(
            flow_nz[["time_bin", "from_node_id", "to_node_id", "x_ijt"]],
            on=["time_bin", "from_node_id", "to_node_id"],
            how="left"
        )

        panel["x_ijt"] = panel["x_ijt"].fillna(0.0)

        panel = panel[
            [
                "time_bin",
                "start_min",
                "end_min",
                "edge_index",
                "edge_id",
                "from_node_id",
                "to_node_id",
                "x_ijt"
            ]
        ]

        panel.to_csv(out_dir / "edge_flow_xijt.csv", index=False)
        flow_for_downstream = panel
    else:
        flow_nz.to_csv(out_dir / "edge_flow_xijt.csv", index=False)
        flow_for_downstream = flow_nz

    missing_rows = [
        {
            "from_node_id": u,
            "to_node_id": v,
            "count": cnt
        }
        for (u, v), cnt in missing_counter.items()
    ]

    missing_df = pd.DataFrame(missing_rows)

    if len(missing_df) > 0:
        missing_df = missing_df.sort_values("count", ascending=False)

    missing_df.to_csv(out_dir / "missing_path_edges.csv", index=False)

    summary = {
        "edge_flow_mode": EDGE_FLOW_MODE,
        "total_agents": total_agents,
        "used_completed_agents": used_agents,
        "bad_agents": bad_agents,

        "total_edge_traversals": total_edge_traversals,
        "used_edge_traversals": used_edge_traversals,
        "missing_edge_traversals": missing_edge_traversals,

        "counted_edge_segments_after_time_filter": counted_edge_segments,
        "skipped_time_segments": skipped_time_segments,
        "bad_time_segments": bad_time_segments,
        "occupancy_bin_updates": occupancy_bin_updates,

        "time_bin_minutes": TIME_BIN_MIN,
        "number_of_time_bins": n_bins,
        "max_time_seen_in_agent_paths": max_time_seen
    }

    return flow_for_downstream, flow_nz, time_df, summary


# ============================================================
# x_it
# ============================================================

def build_node_flow(out_dir, nodes, flow_nz, time_df):
    node_ids = nodes["node_id"].dropna().astype(int).sort_values().unique()

    out_flow = (
        flow_nz
        .groupby(["time_bin", "from_node_id"], as_index=False)["x_ijt"]
        .sum()
        .rename(columns={"from_node_id": "node_id", "x_ijt": "out_flow"})
    )

    in_flow = (
        flow_nz
        .groupby(["time_bin", "to_node_id"], as_index=False)["x_ijt"]
        .sum()
        .rename(columns={"to_node_id": "node_id", "x_ijt": "in_flow"})
    )

    print("Building complete node-time panel...")

    time_idx = pd.DataFrame({
        "time_bin": np.repeat(time_df["time_bin"].values, len(node_ids)),
        "start_min": np.repeat(time_df["start_min"].values, len(node_ids)),
        "end_min": np.repeat(time_df["end_min"].values, len(node_ids))
    })

    node_idx = pd.DataFrame({
        "node_id": np.tile(node_ids, len(time_df))
    })

    panel = pd.concat([time_idx, node_idx], axis=1)

    panel = panel.merge(out_flow, on=["time_bin", "node_id"], how="left")
    panel = panel.merge(in_flow, on=["time_bin", "node_id"], how="left")

    panel["out_flow"] = panel["out_flow"].fillna(0.0)
    panel["in_flow"] = panel["in_flow"].fillna(0.0)
    panel["net_flow"] = panel["out_flow"] - panel["in_flow"]

    panel = panel[
        [
            "time_bin",
            "start_min",
            "end_min",
            "node_id",
            "in_flow",
            "out_flow",
            "net_flow"
        ]
    ]

    panel.to_csv(out_dir / "node_flow_xit.csv", index=False)
    return panel


# ============================================================
# Optional Output_LinkTDMOE.csv processing
# Disabled by default
# ============================================================

def build_moe_features(base_dir, out_dir, flow_nz):
    moe_path = find_file(base_dir, ["output_LinkTDMOE.csv", "Output_LinkTDMOE.csv", "output_linkTDMOE.csv"])

    if moe_path is None:
        return None, None

    moe = read_csv_auto(moe_path)
    moe = clean_colnames(moe)

    required = ["from_node_id", "to_node_id", "timestamp_in_min"]
    for col in required:
        if col not in moe.columns:
            raise ValueError(f"Output_LinkTDMOE.csv is missing required column: {col}")

    moe["from_node_id"] = to_num(moe["from_node_id"]).astype("Int64")
    moe["to_node_id"] = to_num(moe["to_node_id"]).astype("Int64")
    moe["timestamp_in_min"] = to_num(moe["timestamp_in_min"])

    moe = moe.dropna(subset=["from_node_id", "to_node_id", "timestamp_in_min"])
    moe["from_node_id"] = moe["from_node_id"].astype(int)
    moe["to_node_id"] = moe["to_node_id"].astype(int)

    moe["time_bin"] = np.floor(moe["timestamp_in_min"] / TIME_BIN_MIN).astype(int)
    moe["start_min"] = moe["time_bin"] * TIME_BIN_MIN
    moe["end_min"] = (moe["time_bin"] + 1) * TIME_BIN_MIN
    moe["edge_id"] = moe["from_node_id"].astype(str) + "->" + moe["to_node_id"].astype(str)

    numeric_cols = [
        c for c in moe.columns
        if c not in [
            "from_node_id",
            "to_node_id",
            "link_id_from_to",
            "edge_id",
            "time_bin",
            "start_min",
            "end_min"
        ]
    ]

    for c in tqdm(numeric_cols, desc="Converting MOE columns"):
        moe[c] = to_num(moe[c])

    sum_cols = [
        "link_in_volume_number_of_veh",
        "link_out_volume_number_of_veh",
        "link_volume_in_veh_per_hour_per_lane",
        "link_volume_in_veh_per_hour_for_all_lanes",
        "total_energy",
        "total_CO2",
        "total_NOX",
        "total_CO",
        "total_HC"
    ]

    mean_cols = [
        "travel_time_in_min",
        "delay_in_min",
        "density_in_veh_per_distance_per_lane",
        "speed",
        "queue_length_percentage",
        "number_of_queued_vehicles"
    ]

    max_cols = [
        "cumulative_arrival_count",
        "cumulative_departure_count"
    ]

    agg = {}

    for c in sum_cols:
        if c in moe.columns:
            agg[c] = "sum"

    for c in mean_cols:
        if c in moe.columns:
            agg[c] = "mean"

    for c in max_cols:
        if c in moe.columns:
            agg[c] = "max"

    if "day_no" in moe.columns:
        agg["day_no"] = "first"

    print("Aggregating MOE features...")

    grouped = (
        moe
        .groupby(["time_bin", "start_min", "end_min", "from_node_id", "to_node_id", "edge_id"], as_index=False)
        .agg(agg)
    )

    grouped.to_csv(out_dir / "edge_moe_features.csv", index=False)

    if "link_in_volume_number_of_veh" in grouped.columns:
        cmp_df = grouped[
            [
                "time_bin",
                "start_min",
                "end_min",
                "from_node_id",
                "to_node_id",
                "edge_id",
                "link_in_volume_number_of_veh"
            ]
        ].merge(
            flow_nz[["time_bin", "from_node_id", "to_node_id", "x_ijt"]],
            on=["time_bin", "from_node_id", "to_node_id"],
            how="left"
        )

        cmp_df["x_ijt"] = cmp_df["x_ijt"].fillna(0.0)
        cmp_df["agent_minus_moe_link_in"] = cmp_df["x_ijt"] - cmp_df["link_in_volume_number_of_veh"]
        cmp_df["abs_diff"] = cmp_df["agent_minus_moe_link_in"].abs()

        cmp_df.to_csv(out_dir / "edge_flow_vs_moe_check.csv", index=False)
    else:
        cmp_df = None

    return grouped, cmp_df


# ============================================================
# Neighbors
# ============================================================

def dijkstra_k_nearest(source, adjacency, k_nearest=10, max_radius=None):
    dist = {source: 0.0}
    heap = [(0.0, source)]
    result = []

    while heap:
        d, u = heapq.heappop(heap)

        if d > dist.get(u, float("inf")):
            continue

        if max_radius is not None and d > max_radius:
            continue

        if u != source:
            result.append((u, d))

            if max_radius is None and k_nearest is not None and len(result) >= k_nearest:
                break

        for v, w in adjacency.get(u, []):
            nd = d + w

            if max_radius is not None and nd > max_radius:
                continue

            if nd < dist.get(v, float("inf")):
                dist[v] = nd
                heapq.heappush(heap, (nd, v))

    return result


def build_node_neighbors(out_dir, nodes, links):
    adjacency = defaultdict(list)

    for r in links[["from_node_id", "to_node_id", "length"]].itertuples(index=False):
        u = int(r.from_node_id)
        v = int(r.to_node_id)
        length = float(r.length) if pd.notna(r.length) else 1.0
        adjacency[u].append((v, length))

    rows = []

    for r in links[["from_node_id", "to_node_id", "length"]].itertuples(index=False):
        rows.append({
            "node_id": int(r.from_node_id),
            "neighbor_node_id": int(r.to_node_id),
            "neighbor_type": "direct_out",
            "hop_distance": 1,
            "network_distance": float(r.length) if pd.notna(r.length) else np.nan,
            "rank": np.nan
        })

    node_ids = nodes["node_id"].dropna().astype(int).sort_values().unique()

    for src in tqdm(node_ids, desc="Node shortest paths"):
        nearest = dijkstra_k_nearest(
            source=int(src),
            adjacency=adjacency,
            k_nearest=K_NEAREST_NODES,
            max_radius=NODE_DISTANCE_RADIUS
        )

        for rank, (dst, d) in enumerate(nearest, start=1):
            rows.append({
                "node_id": int(src),
                "neighbor_node_id": int(dst),
                "neighbor_type": f"shortest_path_top_{K_NEAREST_NODES}",
                "hop_distance": np.nan,
                "network_distance": d,
                "rank": rank
            })

    neighbors = pd.DataFrame(rows)

    neighbors = neighbors.drop_duplicates(
        ["node_id", "neighbor_node_id", "neighbor_type"]
    )

    neighbors = neighbors.sort_values(
        ["node_id", "neighbor_type", "network_distance", "neighbor_node_id"]
    )

    neighbors.to_csv(out_dir / "node_neighbors.csv", index=False)
    return neighbors


def build_edge_neighbors(out_dir, links):
    incoming = defaultdict(list)
    outgoing = defaultdict(list)
    edge_info = {}

    for r in links[["edge_index", "edge_id", "from_node_id", "to_node_id", "length"]].itertuples(index=False):
        edge_index = int(r.edge_index)
        u = int(r.from_node_id)
        v = int(r.to_node_id)
        length = float(r.length) if pd.notna(r.length) else np.nan

        edge_info[edge_index] = {
            "edge_id": r.edge_id,
            "from_node_id": u,
            "to_node_id": v,
            "length": length
        }

        outgoing[u].append(edge_index)
        incoming[v].append(edge_index)

    rows = []

    def is_reverse_edge(e, n):
        return (
            e["from_node_id"] == n["to_node_id"]
            and e["to_node_id"] == n["from_node_id"]
        )

    def center_distance(e, n):
        if pd.isna(e["length"]) or pd.isna(n["length"]):
            return np.nan
        return 0.5 * e["length"] + 0.5 * n["length"]

    def add_relation(edge_index, neighbor_index, relation_type, shared_node_id):
        if edge_index == neighbor_index:
            return

        e = edge_info[edge_index]
        n = edge_info[neighbor_index]

        rows.append({
            "edge_index": edge_index,
            "edge_id": e["edge_id"],
            "from_node_id": e["from_node_id"],
            "to_node_id": e["to_node_id"],
            "edge_length": e["length"],
            "neighbor_edge_index": neighbor_index,
            "neighbor_edge_id": n["edge_id"],
            "neighbor_from_node_id": n["from_node_id"],
            "neighbor_to_node_id": n["to_node_id"],
            "neighbor_edge_length": n["length"],
            "relation_type": relation_type,
            "shared_node_id": shared_node_id,
            "network_distance": center_distance(e, n),
            "distance_type": "local_connected_edge_center_distance",
            "is_reverse_edge": is_reverse_edge(e, n)
        })

    for edge_index, e in tqdm(edge_info.items(), total=len(edge_info), desc="Edge neighbors"):
        u = e["from_node_id"]
        v = e["to_node_id"]

        for nb in incoming[u]:
            add_relation(edge_index, nb, "upstream", u)

        for nb in outgoing[v]:
            add_relation(edge_index, nb, "downstream", v)

        for nb in outgoing[u]:
            add_relation(edge_index, nb, "share_from_node", u)

        for nb in incoming[v]:
            add_relation(edge_index, nb, "share_to_node", v)

    edge_neighbors = pd.DataFrame(rows)

    if len(edge_neighbors) > 0:
        edge_neighbors = edge_neighbors.drop_duplicates(
            ["edge_index", "neighbor_edge_index", "relation_type"]
        )

        edge_neighbors = edge_neighbors.sort_values(
            ["edge_index", "relation_type", "network_distance", "neighbor_edge_index"]
        )

    edge_neighbors.to_csv(out_dir / "edge_neighbors.csv", index=False)
    return edge_neighbors


# ============================================================
# Wide tables
# ============================================================

def write_wide_tables(out_dir, edge_flow, node_flow):
    if not WRITE_WIDE_TABLES:
        return

    print("Writing edge_flow_xijt_wide.csv...")

    ef = edge_flow.copy()
    ef["var_name"] = "x" + ef["from_node_id"].astype(str) + "-" + ef["to_node_id"].astype(str) + "t"

    edge_wide = (
        ef
        .pivot_table(
            index=["time_bin", "start_min", "end_min"],
            columns="var_name",
            values="x_ijt",
            aggfunc="sum",
            fill_value=0.0
        )
        .reset_index()
    )

    edge_wide.columns.name = None
    edge_wide.to_csv(out_dir / "edge_flow_xijt_wide.csv", index=False)

    print("Writing node wide tables...")

    nf = node_flow.copy()
    nf["var_name"] = "x" + nf["node_id"].astype(str) + "t"

    for value_col, file_name in [
        ("net_flow", "node_flow_xit_net_wide.csv"),
        ("in_flow", "node_flow_xit_in_wide.csv"),
        ("out_flow", "node_flow_xit_out_wide.csv")
    ]:
        wide = (
            nf
            .pivot_table(
                index=["time_bin", "start_min", "end_min"],
                columns="var_name",
                values=value_col,
                aggfunc="sum",
                fill_value=0.0
            )
            .reset_index()
        )

        wide.columns.name = None
        wide.to_csv(out_dir / file_name, index=False)


# ============================================================
# Preview plot
# ============================================================

def write_network_preview(out_dir, nodes, links):
    if not MAKE_NETWORK_PREVIEW:
        return

    try:
        import matplotlib.pyplot as plt
        from matplotlib.collections import LineCollection
    except Exception:
        print("matplotlib is not available. Skipped road_network_preview.png.")
        return

    coord = {
        int(r.node_id): (float(r.x), float(r.y))
        for r in nodes[["node_id", "x", "y"]].dropna().itertuples(index=False)
    }

    segments = []

    for r in tqdm(links[["from_node_id", "to_node_id"]].itertuples(index=False), total=len(links), desc="Preparing network plot"):
        u = int(r.from_node_id)
        v = int(r.to_node_id)

        if u in coord and v in coord:
            segments.append([coord[u], coord[v]])

    if len(segments) == 0:
        return

    fig, ax = plt.subplots(figsize=(10, 10))

    lc = LineCollection(segments, linewidths=0.25, alpha=0.45)
    ax.add_collection(lc)

    xy = nodes[["x", "y"]].dropna()

    if len(xy) <= 20000:
        ax.scatter(xy["x"], xy["y"], s=1, alpha=0.4)

    ax.autoscale()
    ax.set_aspect("equal", adjustable="box")
    ax.set_title("Road Network Preview")
    ax.set_xlabel("x")
    ax.set_ylabel("y")

    fig.tight_layout()
    fig.savefig(out_dir / "road_network_preview.png", dpi=300)
    plt.close(fig)


# ============================================================
# Summary
# ============================================================

def write_summary(out_dir, summary_dict):
    lines = []

    for k, v in summary_dict.items():
        lines.append(f"{k}: {v}")

    with open(out_dir / "processing_summary.txt", "w", encoding="utf-8") as f:
        f.write("\n".join(lines))


# ============================================================
# Main
# ============================================================

def main():
    base_dir = Path(".").resolve()
    out_dir = base_dir / OUTPUT_DIR
    out_dir.mkdir(parents=True, exist_ok=True)

    print("\nStep 1/9: Reading and cleaning nodes...")
    nodes = build_nodes(base_dir, out_dir)
    print(f"Saved nodes_clean.csv. Nodes: {len(nodes)}")

    print("\nStep 2/9: Reading and cleaning directed links...")
    links = build_links(base_dir, out_dir, nodes)
    print(f"Saved links_clean.csv. Directed edges: {len(links)}")

    print(f"\nStep 3/9: Building edge flow x_ijt from output_agent.csv...")
    print(f"Current EDGE_FLOW_MODE = {EDGE_FLOW_MODE}")
    edge_flow, edge_flow_nz, time_df, flow_summary = build_edge_flow(base_dir, out_dir, links)
    print(f"Saved edge_flow_xijt.csv. Rows: {len(edge_flow)}")
    print(f"Saved edge_flow_xijt_nonzero.csv. Nonzero rows: {len(edge_flow_nz)}")

    print("\nStep 4/9: Building node flow x_it...")
    node_flow = build_node_flow(out_dir, nodes, edge_flow_nz, time_df)
    print(f"Saved node_flow_xit.csv. Rows: {len(node_flow)}")

    print("\nStep 5/9: Aggregating Output_LinkTDMOE.csv if available...")

    if USE_MOE_FEATURES:
        moe_features, moe_check = build_moe_features(base_dir, out_dir, edge_flow_nz)

        if moe_features is not None:
            print(f"Saved edge_moe_features.csv. Rows: {len(moe_features)}")

            if moe_check is not None:
                print(f"Saved edge_flow_vs_moe_check.csv. Rows: {len(moe_check)}")
        else:
            print("Output_LinkTDMOE.csv not found. Skipped MOE features.")
    else:
        print("Skipped Output_LinkTDMOE.csv because USE_MOE_FEATURES = False.")

    print("\nStep 6/9: Building node neighbors...")
    node_neighbors = build_node_neighbors(out_dir, nodes, links)
    print(f"Saved node_neighbors.csv. Rows: {len(node_neighbors)}")

    print("\nStep 7/9: Building edge neighbors...")
    edge_neighbors = build_edge_neighbors(out_dir, links)
    print(f"Saved edge_neighbors.csv. Rows: {len(edge_neighbors)}")

    print("\nStep 8/9: Writing wide tables...")
    write_wide_tables(out_dir, edge_flow, node_flow)

    print("\nStep 9/9: Writing network preview...")
    write_network_preview(out_dir, nodes, links)

    summary = {
        "base_dir": str(base_dir),
        "output_dir": str(out_dir),
        "TIME_BIN_MIN": TIME_BIN_MIN,
        "EDGE_FLOW_MODE": EDGE_FLOW_MODE,
        "FORCE_FULL_DAY": FORCE_FULL_DAY,
        "FULL_DAY_MINUTES": FULL_DAY_MINUTES,
        "CLIP_FLOW_TO_TIME_PANEL": CLIP_FLOW_TO_TIME_PANEL,
        "USE_MOE_FEATURES": USE_MOE_FEATURES,
        "number_of_nodes": len(nodes),
        "number_of_directed_edges": len(links),
        "edge_flow_rows": len(edge_flow),
        "edge_flow_nonzero_rows": len(edge_flow_nz),
        "node_flow_rows": len(node_flow),
        "node_neighbor_rows": len(node_neighbors),
        "edge_neighbor_rows": len(edge_neighbors),
    }

    summary.update(flow_summary)
    write_summary(out_dir, summary)

    print("\nDone.")
    print(f"All outputs are in: {out_dir}")


if __name__ == "__main__":
    main()
```

## 3.Output：
```{r}
out_dir <- "processed_real_network/"
```

### 3.1 Graph Topology

**links_clean.csv: **Cleaned directed edge table: Each directed edge is assigned a sequential, zero-based internal index named edge_index.

* <span style="color: blue;">**edge_index**:The unique sequential index number assigned to each edge (link) in the network.

* **from_node_id**: The identification number of the intersection or point where this link begins.

* **to_node_id**: The identification number of the intersection or point where this link ends.

* **length**: The physical distance of the road segment (usually in miles or kilometers).

* **number_of_lanes**: The total count of traffic lanes available on this specific link.

* **speed_limit**: The maximum legal or permitted speed on this link.

* **lane_capacity_in_vhc_per_hour**: The maximum number of vehicles that can pass through a single lane in one hour under ideal conditions.

* **link_type**: A numerical code representing the functional class or category of the road (e.g., highway, arterial, local road).

* **jam_density**: In traffic flow theory, this is the maximum density of vehicles on a road when traffic is completely stopped (bumper-to-bumper).

* **wave_speed**: The speed at which a traffic congestion shockwave propagates backward through the traffic stream.

* **name**: A designated string name or acronym for the road segment.

* **link_type_name**: A descriptive string explaining the functional class of the road.

* **geometry**: The spatial geometric data (like a LineString) used for mapping and GIS visualization.

* **original_geometry**: The raw spatial geometry before any network simplification, snapping, or processing.

* **direction_flag**: Indicates the permitted direction of travel relative to the drawn geometry.

* **original_link_id**: The identification number this road segment had in the source dataset before being imported into this model.

* **original_link_key**: A unique string identifier from the source data, often combining the ID and direction .

* <span style="color: blue;">**edge_id**: A readable string concatenating the from-node and to-node to visually represent the connection (e.g., "1->4106").

```{r}
links_clean <- read.csv(paste0(out_dir, "links_clean.csv"), nrows = 10, check.names = FALSE)
links_clean
```

### 3.2 Spatio-Temporal Flow Tensor
According to a time slice of 5 minutes, the discrete vehicle trajectories are segmented into time series data:

**edge_flow_xijt.csv: **The traffic volume passing through a certain section of the road has been summarized.

* **time_bin: **A sequential integer representing a specific time interval or "bucket" during the simulation period.

* **start_min: **The starting time of this specific time bin, measured in minutes from the beginning of the simulation.

* **end_min: **The ending time of this specific time bin, measured in minutes.

* **edge_index: **The internal numeric identifier for the road segment (same as in your previous static tables).

* **edge_id: **The descriptive identifier showing the connection from origin node to destination node (e.g., "1->4106").

* **from_node_id: **The ID of the node where this link starts.

* **to_node_id: **The ID of the node where this link ends.

* <span style="color: blue;">**x_ijt: **A standard variable notation in transportation engineering representing the traffic flow (number of vehicles) on link from node i to node j during time interval t.

```{r}
flow_panel <- read.csv(paste0(out_dir, "edge_flow_xijt.csv"), nrows = 10, check.names = FALSE)
flow_panel
```

**node_flow_xit.csv: **The traffic volume passing through a certain intersection has been summarized.

* **node_id: **The unique identifier for a specific intersection, junction, or zone centroid in the network.

* **in_flow: **The total number of vehicles entering this specific node during this time bin.

* **out_flow: **The total number of vehicles leaving this specific node during this time bin.

* <span style="color: blue;">**net_flow: **The net difference in traffic at this node (usually calculated as Outflow - Inflow, or representing net traffic generated by a source node).

```{r}
node_flow <- read.csv(paste0(out_dir, "node_flow_xit.csv"), nrows = 10, check.names = FALSE)
node_flow
```

### 3.3 Basic Adjacency
**node_neighbors.csv: **It summarizes the other intersections directly connected to a certain intersection.

* **node_id: **The identification number of the starting point or intersection currently being analyzed.

* <span style="color: blue;">**neighbor_node_id: **The identifier of the node that is reachable from the reference node_id.

* <span style="color: blue;">**neighbor_type: **Describes the nature of the connection between the reference node and the neighbor.

* <span style="color: blue;">**hop_distance: **The topological distance, meaning the number of links (edges) that must be traversed to reach the neighbor. For direct_out types, this is exactly 1. 

* **network_distance: **The physical length or accumulated travel cost to go from the node_id to the neighbor_node_id along the actual road network.

* **rank: Distance Ranking. **The sorting order of the neighbors based on their network_distance (1 being the absolute closest). 

```{r}
node_nb <- read.csv(paste0(out_dir, "node_neighbors.csv"), nrows = 10, check.names = FALSE)
node_nb
```

**edge_neighbors.csv: **It summarizes other sections directly connected to a certain road section, including the upstream and downstream.

* **edge_index: **The internal numeric ID of the primary edge being analyzed.

* **edge_id: **Reference Edge String ID. The descriptive ID of the reference edge (e.g., "1->4106").

* **from_node_id: **The ID of the node where the reference edge begins.

* **to_node_id: **The ID of the node where the reference edge ends.

* **edge_length: **The physical length of the primary edge.

* <span style="color: blue;">**neighbor_edge_index: **The internal numeric ID of the adjacent or related edge.

* <span style="color: blue;">**neighbor_edge_id: **The descriptive connection string for the neighbor edge (e.g., "4106->1").

* <span style="color: blue;">**neighbor_from_node_id: **The originating node of the neighboring edge.

* <span style="color: blue;">**neighbor_to_node_id: **The terminating node of the neighboring edge.

* **neighbor_edge_length: **The physical length of this specific neighboring edge.

* <span style="color: blue;">**relation_type: **Describes how the two edges connect:

  <span style="color: blue;">**downstream: **The reference edge flows directly into the neighbor edge (tail-to-head).

  <span style="color: blue;">**share_from_node: **Both edges start at the same node (diverging).

  <span style="color: blue;">**share_to_node: **Both edges end at the same node (merging).

* **shared_node_id: **The specific intersection or node that connects the two edges.

* **network_distance: **The computed distance between the two edges based on the defined distance_type.

* **distance_type: **Shows how the network_distance was measured. local_connected_edge_center_distance means the distance is measured from the midpoint of the reference edge to the midpoint of the neighbor edge.

* **is_reverse_edge: **Is Reverse Edge Flag. A boolean value (True or False). If True, it means the neighbor edge is the exact opposite flow direction of the reference edge (e.g., Reference is A->B, Neighbor is B->A, making them two sides of the same physical road).

```{r}
edge_nb <- read.csv(paste0(out_dir, "edge_neighbors.csv"), nrows = 10, check.names = FALSE)
edge_nb
```

### 3.4 ML-Ready Wide Tables
**edge_flow_xijt_wide.csv: **The wide table uses each time bin as a row, each road segment (e.g., x1-2t, x2-3t) as a column, and the values in the cells represent the corresponding traffic flow.
```{r}
temp <- read.csv(paste0(out_dir, "edge_flow_xijt_wide.csv"), 
                 nrows = 10,  
                 check.names = FALSE)
sub_matrix <- temp[, 1:7]
sub_matrix
```


## 4.Visualization
An interactive map containing extensive micro-level road segments and dynamic traffic data.

### 4.1 Static Traffic Flow Snapshot

This map illustrates the traffic flow distribution across the entire road network at a specific moment (Time Bin 107). It intuitively visualizes the congestion levels of various road segments using color-coded highlighted lines.

* **Interaction Guide**：The map supports free zooming and panning. Click on any highlighted road segment to view its specific flow volume (x_ijt), origin and destination node IDs, and road type.
* 👉 **[Click here to view](processed_real_network/visualizations/xijt_leaflet_time_bin_107_amap-satellite-labels.html)**

### 4.2 Dynamic Traffic Flow Evolution Map

This map integrates flow data across all time bins, designed to demonstrate the spatial and temporal propagation and dissipation of traffic congestion.

* **Interaction Guide**：Drag the time slider to quickly jump to any specific time bin, or click the "Play" button to automatically animate the chronological evolution of the traffic flow.

* 👉 **[Click here to view：](processed_real_network/visualizations/xijt_dynamic_leaflet_amap-satellite-labels.html)**