# Current five-family simulation samplers

This file replaces the *development workflow* formerly provided by the frozen
`4gibbs.Rmd`; it does not overwrite that historical source.  Load
`2helpers.Rmd` first.  The sampler functions themselves are maintained in
`R/gmde-state-update.R`, `R/gmde-classifier.R`, and `R/gmde-mcmc.R`.

## One current MCMC sweep

The implementation follows the current Overleaf manuscript in this order:

1. Compute `N[k]`, `S[k, t]`, and the fixed-within-proposal
   `r[k, t] = rho * max(S[k, t], 1)`.
2. For each nonempty expert, draw Pólya--Gamma variables, make one complete
   path proposal with information-form FFBS, and apply one Poisson/NB
   Metropolis correction to the entire path.  Empty experts are drawn from the
   DLM prior without evaluating `log(N[k])`.
3. Update the allocation model: one joint ESS transition for a graph/Euclidean
   GP gate, one Dirichlet draw for MoDE, or a random-scan single-site Gibbs
   sweep for fixed-beta Potts-MDE.
4. Combine the same Poisson expert likelihood with that allocation model and
   update labels.  The Potts full conditional is
   `count log likelihood + beta * sum_j W[i,j] * I(Z[j] == k)`.
5. Relabel by increasing expert mean intensity and store MH, ESS/Potts, rho,
   occupancy, and timing diagnostics.

The five families differ only in the allocation part:

| method | allocation input | allocation update |
|---|---|---|
| GMDE-W | rank-40 weighted-road Matérn basis | joint ESS |
| GMDE-C | rank-40 binary-connectivity Matérn basis | joint ESS |
| Euc-MDE | rank-40 Euclidean Matérn basis | joint ESS |
| MoDE | common symmetric `Dirichlet(1/10, ..., 1/10)` weights | Gibbs |
| Potts-MDE | approved weighted road graph and fixed beta | random-scan single-site Gibbs |

## Public entry points

```{r current-sampler-interface, eval=FALSE}
## Fixed-rho run.  rho is explicit because r_tune from the old sampler has a
## different meaning and is rejected rather than silently converted.
fit_gmde <- run_gmde_mcmc(
  Y = Y,
  Fmat = Fmat,
  Phi = Phi,
  K = K,
  n_iter = n_iter,
  burn = burn,
  rho = rho,
  pg_backend = "devroye-exact",
  seed = chain_seed
)

fit_mode <- run_nograph_mcmc(
  Y = Y,
  Fmat = Fmat,
  K = K,
  alpha_pi = alpha_pi,
  n_iter = n_iter,
  burn = burn,
  rho = rho,
  pg_backend = "devroye-exact",
  seed = chain_seed
)

fit_potts <- run_potts_mcmc(
  Y = Y,
  Fmat = Fmat,
  K = K,
  potts_W = W_road,
  potts_beta = fixed_beta,
  n_iter = n_iter,
  burn = burn,
  rho = rho,
  pg_backend = "devroye-exact",
  seed = chain_seed
)
```

All entry points share exactly the same state-path kernel and DLM priors.
GMDE-W, GMDE-C, and Euc-MDE all call `run_gmde_mcmc()`; only `Phi` changes.
`countdlm_road_fit_method()` is the fail-closed dispatcher used by the quick
workflow.  It accepts only the five exact method names, so a misspelling cannot
silently fall through to MoDE.

At fixed beta, Potts label Gibbs updates do not require the global normalizing
constant.  That constant is needed for an observed-data marginal and for
learning beta, however.  The sampler therefore stores the valid unnormalized
complete-data diagnostic (Poisson count term plus Potts energy), sets the
Potts observed-log-likelihood trace to `NA`, and never substitutes a product
of node conditionals.  Sensitivity across beta must use the prespecified
label-free rule, not these unnormalized values.

For the Beijing application, `run_gmde_mcmc_heterogeneous()` applies the same
PG → information-FFBS → whole-path MH update separately to each expert's
`F_list`, `m0_list`, `C0_list`, `G_list`, and `W_list`, followed by the same
joint classifier ESS.  Heterogeneous expert specifications identify the class
labels, so this entry point performs no within-chain relabeling and defaults to
`order_initial_labels = FALSE`.  It currently supports a time-varying design
matrix for each expert with expert-specific but time-constant `G` and `W`;
fully time-varying `G[k,t]`/`W[k,t]` remains an explicit interface extension.

```{r current-heterogeneous-interface, eval=FALSE}
fit_beijing <- run_gmde_mcmc_heterogeneous(
  Y = Y,
  F_list = F_list,
  Phi = Phi,
  K = K,
  n_iter = n_iter,
  burn = burn,
  m0_list = m0_list,
  C0_list = C0_list,
  G_list = G_list,
  W_list = W_list,
  rho = approved_integer_rho,
  pg_backend = "devroye-exact",
  seed = chain_seed
)
```

## Independent fixed-rho calibration

The approved road pilot does not change `rho` inside an MCMC chain.  Its first
phase instead runs 42 separate fixed-rho branches: seven method variants by two
initializations by `rho = 1, 2, 4`.  Every branch has 120 transitions; the first
60 are an unscored settling period and only transitions 61--120 contribute to
the calibration score.  Within a variant-initialization pair, the three rho
branches use the same registered method seed and byte-identical initial
allocation, state paths, and classifier state.  They never inherit a terminal
state from one another.

The public wrapper registers and executes this complete protocol:

```{r current-rho-calibration-interface, eval=FALSE}
calibration_cfg <- countdlm_road_calibration_config(
  context_file = approved_context_file,
  output_dir = new_external_output_directory
)

calibration_result <- countdlm_road_calibration_pilot(
  config = calibration_cfg,
  repository_root = repository_root
)
```

The score pools raw accepted information-weighted movement and raw complete
state-update seconds before division.  State-update time includes PG sampling,
information-form FFBS, and the whole-path MH correction.  Each non-Potts
record has weight one and each of the three fixed-beta Potts records has weight
one third.  The smallest candidate within 5% of the largest pooled efficiency
is selected only if every branch has an accepted proposal with positive
information-weighted movement, both initialization strata and both halves of
the scoring window select the same rho, every branch's largest
single-transition movement share is at most 20%, and the shared rho retains at
least 80% of each method family's best efficiency.  A failed audit is a
completed, unresolved Phase-1
outcome; it never starts Phase 2.  A resolved rho is held fixed in the 14-task
short stability phase and in any later evaluation run.

Full-path proposals are implemented.  The optional temporal blocking mentioned
in the appendix is not automatically enabled because its threshold and block
design have not been specified.

## Required diagnostics

Every fit records:

- `state_accepted`, `state_log_acceptance`, and accepted weighted movement;
- per-expert complete `state_update_seconds`, PG time, and the sum and maximum
  of the realized PG shapes;
- the complete fixed `state_rho` trace, registered initialization, and
  calibration audit tables;
- joint-ESS bracket and likelihood evaluation counts;
- the Pólya--Gamma backend and `algorithm_exact` flag;
- the new sampler version, state-update identity, and classifier-update
  identity.

For the noninferential runtime quick test, truth labels are not supplied to the
sampler and all truth-based recovery scores remain uncomputed.  Potts-MDE is
run at every beta in the short provisional grid solely to measure the full
internal computational envelope.

Archived 2026-08-22 fits do not contain this contract and must never be resumed
or relabelled as outputs of the current sampler.
