# Current simulation status: K=10 conditional-allocation Debug

This handoff replaces the earlier K=6 entry note. Scientific functions remain
in `R/*.R`; opening or knitting this file never launches computation.

## Status on 3 September 2026

The planned road experiment uses `n=100`, `T=168`, `K_true=5`, an overfitted
`K_fit=10`, graph rank `m=40`, fixed `rho=1`, exact Devroye Polya--Gamma draws,
information-form FFBS with a whole-path Poisson Metropolis correction, and
joint elliptical slice sampling for the three graph-gating variants.

The most recent truth-blinded passive conditional-allocation diagnostic did not
pass its fail-closed gate:

- 11 of 12 registered tasks completed;
- `GMDE-W-mode-A-seed-2`, seed 2026094102, failed after about 307 seconds;
- the error was `Poisson-binomial threshold recursion failed its mass audit.`;
- no formal simulation was launched or authorized.

This failure is in deterministic diagnostic work immediately before a label
draw. The current evidence neither proves nor disproves correctness of the
underlying MCMC transition. It must be diagnosed without changing K, rho,
seeds, starts, DGP, graph or scientific thresholds.

## Self-contained handoff entry points

Start R in the `graphMoDE` directory.

```{r input-audit, eval=FALSE}
source("scripts/check_inputs.R")
```

```{r focused-tests, eval=FALSE}
source("scripts/run_tests.R")
```

```{r reproduce-single-failure, eval=FALSE}
source("scripts/reproduce_k10_failure.R")
```

The final command runs only the known failing chain and installs an in-memory,
non-random wrapper around `gmde_poisson_binomial_threshold()`. On failure it
saves the first probability vector and recursion state in the git-ignored
`debug-output/` directory. It does not edit the source file or require the
large K10/K6 parent archives.

## Fixed comparison boundary

| method | allocation structure |
|---|---|
| GMDE-W | weighted road qNN graph basis |
| GMDE-C | binary road-connectivity graph basis |
| Euc-MDE | Euclidean Matérn basis |
| MoDE | graph-free global Dirichlet mixture |
| Potts-MDE | weighted road Potts field |

These five methods use the same dynamic Poisson expert structure. A common
`K_fit=10` is an overfitted comparison because reversible-jump MCMC is not being
used; it does not make the allocation priors identical. PNARM and AR(1) latent
class remain external model comparisons and are not bundled here.

## Gate before any formal run

A repair must capture and explain the numerical failure, pass exact-enumeration
and stress tests, complete the failing chain without warning, preserve its
scientific trace and RNG exactly, and then pass all 12 registered K=10 tasks
against their frozen trace hashes. Simply loosening the `1e-12` mass threshold
is not sufficient. Full criteria are in `debug/KNOWN_ISSUE.md`.

